### 2024-02-11 paper/paper.tex
feat: done first draft of paper

\documentclass[letterpaper]{article}
\usepackage[top=1in, bottom=1.25in, inner=1.25in, outer=1.25in]{geometry}
\usepackage[style=authoryear-comp]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{float}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{booktabs}

\title{Using Bayesian Regression to Quantify Sexual Dimorphism in Extinct Taxa}
\author{Eric Campbell}
\begin{document}
\maketitle

\newcommand{\species}[1]{\textit{#1}}
\newcommand{\tyran}{\species{Tyrannosaurus rex}{}}
\newcommand{\psit}{\species{Psittacosurus lujiatunensis}{}}
\newcommand{\maia}{\species{Maiasaura peeblesorum}{}}
\newcommand{\normal}[2]{\ensuremath{\mathcal{N}\left(#1, #2\right)}}

\section{Introduction}
Sexual dimorphism is the difference in size, colour, or presence of a feature between different sexes in a species. For instance, generally human males are larger than females, male mallard ducks are colourfully ornamented while females are drab, and male deer have antlers while females do not. Sexual dimorphism is very common in extant species, but detection of sexual dimorphism in extinct taxa, especially vertebrates, has been more challenging. Essentially, there are two difficulties in determining sexual dimorphism in extinct taxa: the `sexual' part and the `dimorphism' part. Determining the sex of the individual fossil, in the absence of rare features (such as medullary bone or bacula) is extremely challenging \parencite{saittaEffectSizeStatistical2020}. Similarly, determining the mass or size of a feature from a fossil (such as those of dinosaurs) can be difficult \parencite[p.~126]{brusatte2012}. When trying to determine the level of sexual dimorphism, these problems compound each other.

There are several analytical methods which are commonly used. However, each of these has their weaknesses. The use of $t$ tests (for differences in the mean) or Hartigans' dip test (for unimodality) can suffer from low statistical power \parencite{mallonRecognizingSexualDimorphism2017} and in the case of $t$ tests a further difficulty is the prolonged growth period of most dinosaurs \parencite{honeProtractedGrowthImpedes2017}. As a result, positive results for dimorphism in dinosaurs are rare.

However, a proposed method in \cite{saittaEffectSizeStatistical2020} attempts to sidestep these difficulties by explicitly constructing growth curves for the different sexes. Herein is proposed a modification to that method in which Bayesian regression is used to recover a distribution of possible growth curves for each sex and subsequently applied to calculate the level of dimorphism.

\section{Methods}
The modification to the method in \cite{saittaEffectSizeStatistical2020} is presented below.

\begin{table}[H]
    \centering
    \caption{Method Comparison}
    \begin{tabularx}{\textwidth}{XX}
        \toprule
        \multicolumn{1}{c}{\cite{saittaEffectSizeStatistical2020}} & \multicolumn{1}{c}{Modification} \\
        \midrule
        Gather data: age (or a correlate) and character of interest (e.g. length) & \\
        Fit growth curve to population as a whole & \\
        Predict sex by assigning all samples above the population curve to one sex and all below to the other. & \\
        Fit separate growth curves to each predicted sex & Create a posterior distribution for sex-specific parameters (Bayesian regression) \\
        Calculate maximum likelihood level of dimorphism & Calculate posterior distribution for dimorphism \\
        \bottomrule
    \end{tabularx}
\end{table}

In both methods, the amount of dimorphism is calculated as the difference in the asymptotes of the growth curves.

\subsection{Method Validation}

Validating the method began with a simulated population of American alligators (\species{Alligator mississippiensis}). The original von Bertalanffy growth curves were determined in \cite{wilkinsonGrowthRatesAmerican1997} and a simplified model using a constant standard deviation (rather than sex-specific standard deviation of the form $\alpha \log(\text{mean mass at age}) + \beta$) was used to generate different samples. The final model was

\begin{align*}
\text{Length}_{ m / f } &\sim \mathcal{N}\left(\mu_{ m / f }, \sigma\right) \\
\mu_m &= 3.79 * \left(1 - 0.94e^{-0.0695 \ast \text{age}}\right) \\
\mu_f &= 2.78 * \left(1 - 0.91e^{-0.0926 \ast \text{age}}\right) \\
\sigma &= 0.25
\end{align*}

For the von Bertalanffy equation
$$
\text{Length} = L(1 - Ae^{-K \ast \text{age}})
$$

the parameter $L$ is the asymptotic length, and so the actual level of sexual dimorphism is $\SI{3.79}{\m} - \SI{2.78}{\m} = \SI{1.01}{\m}$.

\begin{figure}
	\centering
	\includegraphics[width = \textwidth]{images/alligatorMethod.png}
	\caption{Simulated Alligator Populations \& Method}
	\label{fig:alligatorSim}
\end{figure}

 A Bayesian model with wide priors centred around the population-level curve values was used to recover the values \parencite{rCore, rstan}.

\begin{align*}
\text{Length}_{m/f,i} &\sim \normal{\mu_{m/f, i}}{\sigma} \\
\mu_{m/f, i} &= \text{von Betlananffy}(\text{age}_i, L_{ m/f }, A_{ m/f }, K_{ m/f }) \\
L_{ m/f } &\sim \normal{\text{population L}}{0.5} \\
A_{ m/f } &\sim \normal{\text{population A}}{0.025} \\
K_{ m/f } &\sim \normal{\text{population K}}{0.05} \\
\sigma &= 0.25 \\
\end{align*}

Since the priors used for the male and female parameters are identical (and initially have means equal to the population-level parameters), the results are slightly biased toward a finding of minimal or no sexual dimorphism.

Both when using only single sex (female) or when including both, the model was able to recover all of the population parameters with a high degree of accuracy (in all cases within the 95\% credible interval for the posterior of each parameter).

The sample size also affects the ability of the method to recover the true values. The model was run with several different sample sizes and the posterior distribution for the level of dimorphism $L_m - L_f$ is shown below.

\begin{figure}[H]
	\centering
	\includegraphics[width = \textwidth]{images/alligatorSampleSize.png}
	\caption{How different sample sizes affect the estimation of the level of dimorphism}
	\label{fig:alligatorSampleSize}
\end{figure}

This method reliably generates mean levels which are close to the true value and the 95\% credible intervals overlap it as well. The general pattern of approaching the value from below is due to the influence of the prior (centred at zero); as the sample size becomes larger they drag the posterior toward the correct value.

We can also ask about how the magnitude of dimorphism affects our ability to detect it. For this, the female parameters were kept at their original value and simulated male populations were created with an effect size $E$ representing the scaled difference between the actual male and female parameters. An effect size of $E = 0$ means that the male and female populations are identical, $E = 1$ is the natural level of dimorphism, and $E = 2$ is twice the natural level of dimorphism. The model was then run and the error in the level of dimorphism was calculated.

\begin{figure}[H]
	\centering
	\includegraphics[width = \textwidth]{images/alligatorEffectSize.png}
	\caption{Effect of sample size on estimated dimorphism level}
	\label{fig:alligatorEffectSizes}
\end{figure}

There is a tendency to overestimate dimorphism when it is small, but converges to the correct value once it reaches a large enough size. Note that a significant contributor to the error in dimorphism estimation is the inaccuracy of our naive sex predictor. By plotting the accuracy of the dimorphism estimation against the computed accuracy in sex prediction, we can see a clear relationship.

\begin{figure}[H]
	\centering
	\includegraphics[width = \textwidth]{images/alligatorSexPredictionAccuracyDimorphismError.png}
	\caption{Relationship between the error in dimorphism estimation and the accuracy of sex prediction}
	\label{fig:alligatorSexPredictionError}
\end{figure}

Overall, the results of the simulation show that this method is reliable, with caveats that at low sample sizes or levels or dimorphism we need to be especially skeptical of the results.

\section{Results}

Once the method had been validated, the same method was used to calculate the posterior distribution for sexual dimorphism for three species of dinosaur: \maia{}, \psit{}, and \tyran{}. The data used were compiled in \cite{saittaEffectSizeStatistical2020} and were originally from \cite{woodwardMaiasauraModelOrganism2015} (\maia), \cite{ericksonFlawedAnalysisResponse2015}  (\psit), and \cite{ericksonGigantismComparativeLifehistory2004}, \cite{hornerAgeGrowthDynamics2004}, and \cite{leeSexualMaturityGrowing2008} (\tyran).

In each case, a logistic growth curve for mass against age with a constant standard deviation was used.

$$
\text{logistic}(\text{age}, L, q, k) = \frac{L}{1 + e^{q+k \ast \text{age}}}
$$

Since $L$ is the asymptotic mass, the level of dimorphism is $L_l - L_s$, where here $l$ represents the larger sex and $s$ represents the smaller one. For each species, priors were chosen again centred around the population level parameters and with a wide enough standard deviation to cover all of the existing data.

For each species, the prior 95\% quantiles for randomly generated populations, along with the actual data, are displayed, along with a selection of posterior growth curves.

\begin{figure}[H]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/maiasauraPrior.png}
  \end{minipage}
  \begin{minipage}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/maiasauraPosterior.png}
  \end{minipage}
    \label{fig:maiasauraPriorPosterior}
    \caption{\maia{} Prior and Posterior Estimates}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/psittacosaurusPrior.png}
  \end{minipage}
  \begin{minipage}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/psittacosaurusPosterior.png}
  \end{minipage}
    \label{fig:psittacosaurusPriorPosterior}
    \caption{\psit{} Prior and Posterior Estimates}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/tyrannosaurPrior.png}
  \end{minipage}
  \begin{minipage}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/tyrannosaurPosterior.png}
  \end{minipage}
    \label{fig:tyrannosaurPriorPosterior}
    \caption{\tyran{} Prior and Posterior Estimates}
\end{figure}

The posterior curves are biologically plausible and in line with both the data and our understanding of physiology; none of the values are immediately out of the realm of possibility.

Of course, we can also compare the levels of dimorphism as the larger sex's size as a percent of the smaller one (e.g. a dimorphism level of 50\% would mean that the larger sex was 50\% larger than the smaller).

\begin{figure}[H]
	\centering
	\includegraphics[width = 0.9\textwidth]{images/combinedDimorphism.png}
	\caption{Dimorphism Levels}
	\label{fig:combinedDimorphism}
\end{figure}

From this, we can see strong evidence for the \maia{} and \psit{} dimorphism, while the \tyran{} displays either no or a very small amount of dimorphism.

\section{Discussion}

As shown above, the modification of the method in \cite{saittaEffectSizeStatistical2020} using Bayesian regression to calculate the posterior distributions for sex-specific growth curves and the level of sexual dimorphism is generally reliable and useful way to quantify dimorphism in extinct populations. While it shares some weakness with with the original method, it also has several notable advantages. One is that by carrying uncertainty through all parts of modelling, the final result contains more information about the process \parencite{mcelreathStatisticalRethinkingBayesian2020}. Another is that by incorporating prior knowledge, we can constrain our final result to be biologically plausible.

Despite these advantages, there remain many area in which this method could be improved. The most critical, as noted in \cite{saittaEffectSizeStatistical2020}, is sex determination. As shown by Figure \ref{fig:alligatorSexPredictionError} sex determination accuracy was a strong predictor of the error in the level of dimorphism. There are two complementary paths which should be taken towards alleviating this issue. The first is the incorporation of the uncertainty in sex determination into the posterior curves generated. At the moment we behave as though the sex that we predict is correct, with no uncertainty, when the reality is that this is a significant source of error. This would result in widening the posterior distributions for the levels of dimorphism, but would not address the underlying issue. For that, we should look at alternate means of predicting sex, such as cluster analysis involving traits other than the one that we are looking at.

Determining levels of sexual dimorphism when both sex and size determination are difficult is naturally a difficult problem, and the method here, while offering an incremental improvement over existing methods, is certainly no panacea. Further efforts, both on the statistical and palaeontological side of the equation, will be required in order to improve our understanding of sexual dimorphism within extinct taxa.

\printbibliography[title=Bibliography]
\end{document}

### 2024-02-11 paper/code/alligatorMethod.R

@@ -1,0 +1,25 @@
+source("functions.R")
+
+# generate the sample
+num_samples <- 1e3
+combined_data <- generate_combined_alligator_sample(generate_male_sample, generate_female_sample, num_samples)
+
+population_fit <- generate_vb_curve_fit(combined_data)
+population_params <- coef(population_fit)
+
+curve_ages <- seq(1, ALLIGATOR_MAX_LIFESPAN, length.out = 100)
+curve_lengths <- generalized_von_bertalanffy(curve_ages, L = population_params[['L']], A = population_params[['A']], K = population_params[['K']])
+curve_data <- data.frame(age = curve_ages, length = curve_lengths)
+
+p <- ggplot(combined_data, aes(age, length)) +
+    geom_point(aes(shape = sex, colour = sex)) +
+    geom_line(data = curve_data, mapping = aes(age, length), linewidth = 2) +
+    annotate('label', label = "Predicted Male", x = 25, y = 3.7, size = unit(8, 'pt'), fill = 'white', label.size = NA) +
+    annotate('label', label = "Predicted Female", x = 25, y = 1.2, size = unit(8, 'pt'), fill = 'white', label.size = NA) +
+    annotate('label', label = "Population Curve", x = 35, y = 2.8, size = unit(8, 'pt'), fill = 'white', label.size = NA) +
+    scale_colour_grey() +
+    scale_fill_grey() +
+    custom_theme() +
+    labs(x = "Age (years)", y = "Length (m)", title = "Alligator Population and Curve", colour = "Sex", shape = "Sex")
+ggsave("../images/alligatorMethod.png", plot = p,  width = 15, height = 8)
+print("Done")

### 2024-02-11 paper/code/dinosaurs.R

@@ -1,0 +1,447 @@
+source("functions.R")
+set.seed(2024)
+
+#### Maiasaura
+data <- read.csv('data/Maiasaura.csv')
+head(data)
+
+maiasaura <- data.frame(
+    age = data$Age..years. + data$Age.shift..years.,
+    mass = data$Fraction.multiplied.to.ROM.44770.body.mass..kg.
+)
+
+maiasaura_plot <- ggplot(maiasaura, aes(age, mass)) +
+    geom_point() +
+    labs(x = "Age (years)", y = "Mass (kg)", title = "Maiasaura peeblesorum") +
+    custom_theme()
+
+initial_maiasaura_params <- list(
+    L=2500,
+    k=0.5,
+    q=10
+)
+
+population_fit <- generate_logistic_curve_fit(maiasaura, initial_params = initial_maiasaura_params)
+population_params <- coef(population_fit)
+
+# generate the priors plot
+num_samples <- 1e3
+Ls <- rnorm(num_samples, population_params[['L']], sd = 500)
+ks <- rnorm(num_samples, population_params[['k']], sd = 0.0125)
+qs <- rnorm(num_samples, population_params[['q']], sd = 0.4)
+sigmas <- rnorm(num_samples, 200, 50)
+
+curve_data <- data.frame(age = numeric(), length = numeric())
+curve_ages <- seq(min(maiasaura$age), max(maiasaura$age), by = 0.5)
+for (i in 1:1e3) {
+    index <- sample(1:num_samples, size = 1)
+    L <- Ls[index]
+    k <- ks[index]
+    q <- qs[index]
+    sigma <- sigmas[index]
+
+    curve_mass_mean <- generalized_logistic(curve_ages, L = L, k = k, q = q)
+    curve_mass <- rnorm(length(curve_mass_mean), mean = curve_mass_mean, sd = sigma)
+    curve_data <- rbind(
+        curve_data,
+        data.frame(age = curve_ages, mass = curve_mass)
+    )
+}
+
+range_df <- data.frame(age = numeric(), lower = numeric(), upper = numeric())
+for (age in unique(curve_data$age)) {
+    relevant <- curve_data[abs(curve_data$age - age) < 0.1, ]
+    masses <- relevant$mass
+    lower <- quantile(masses, c(0.025))
+    upper <- quantile(masses, c(0.975))
+    range_df <- rbind(
+        range_df,
+        data.frame(
+            age = age,
+            lower = lower,
[…]

### 2024-02-11 paper/code/functions.R

@@ -1,0 +1,118 @@
+
+library(ggplot2)
+library(FSA) # for the vbStart function to find good parameters for the von Bertalanffy function
+library(minpack.lm) # a more robust version of nls for non-linear curve fitting to avoid problems with e.g. very small sample sizes
+library(rstan)
+
+options(mc.cores = parallel::detectCores())
+rstan_options(auto_write = TRUE)
+
+source("constants.R")
+
+custom_theme <- function() {
+  theme_minimal() +
+    theme(
+      panel.background = element_rect(fill = "white"),
+      panel.grid.major = element_line(color = alpha("black", 0.5), linetype = "dotted", linewidth = 0.5),
+      panel.grid.minor = element_blank(),
+      axis.text = element_text(size = 12),  # Adjust the font size of axis labels
+      axis.title = element_text(size = 16),  # Adjust the font size of axis titles
+      plot.title = element_text(size = 20, hjust = 0.5),  # Adjust the font size and center the plot title
+      plot.subtitle = element_text(size = 16, hjust = 0.5)  # Adjust the font size and center the plot subtitle
+    )
+}
+
+paper_colours <- function() {
+    scale_colour_grey() +
+    scale_fill_grey()
+}
+
+poster_colours <- function() {
+
+}
+
+generalized_von_bertalanffy <- function(age, L, A, K) {
+    L * (1 - A * exp(-K * age))
+}
+
+generalized_logistic <- function(age, L, q, k) {
+    L / (1 + exp(q + k * age))
+}
+
+generate_initial_vb_params <- function(df, debug = FALSE) {
+    initial_params_raw <- tryCatch({vbStarts(df$length ~ df$age)},
+        error = function(e) {
+            if (debug) {
+                cat("Error getting initial von Bertalanffy parameters for data", conditionMessage(e))
+            }
+            NULL
+        }
+    )
+
+    if (is.null(initial_params_raw)) return(NULL)
+
+    # now convert to my parameterization
+    # I use y = Linf * (1 - A e ^ (-Kt) )
+    # they use y = Linf * (1 - e^(-K (t - t0)))
+    # -> A = e^K t0
+    initial_params <- list(
+        L = initial_params_raw$Linf,
+        K = initial_params_raw$K,
+        A = exp(initial_params_raw$K * initial_params_raw$t0)
+    )
+    initial_params
+}
+
+generate_vb_curve_fit <- function(data) {
[…]

### 2024-02-11 paper/code/alligatorMethod.R
fix: some typos and minor errors

@@ -20,6 +20,6 @@ p <- ggplot(combined_data, aes(age, length)) +
     scale_colour_grey() +
     scale_fill_grey() +
     custom_theme() +
-    labs(x = "Age (years)", y = "Length (m)", title = "Alligator Population and Curve", colour = "Sex", shape = "Sex")
+    labs(x = "Age (years)", y = "Length (m)", title = "Alligator Population and Curve", colour = "Actual Sex", shape = "Actual Sex")
 ggsave("../images/alligatorMethod.png", plot = p,  width = 15, height = 8)
 print("Done")

### 2024-02-12 paperAndPoster/poster.tex
began work on poster

\documentclass[a0paper, landscape]{tikzposter} % See Section 3
\title{Title} \institute{Inst} % See Section 4.1
\author{Auth} \titlegraphic{Logo}
\usetheme{Basic} % See Section 5

\begin{document}
\maketitle % See Section 4.1
\block{BlocktitleA}{Blocktext} % See Section 4.2
\begin{columns} % See Section 4.4
\column{0.3} % See Section 4.4
\block{BlocktitleB}{Blocktext}
\column{0.7}
\block{BlocktitleC}{Blocktext}
\note{Notetext} % See Section 4.3
\end{columns}
\end{document}

### 2024-02-12 paper/code/alligatorEffectSize.R

@@ -1,111 +1,0 @@
-source("functions.R")
-
-set.seed(2024)
-alpha <- 0.05
-num_samples <- 1e3 / 2
-effect_sizes <- seq(0, 2, length.out = 10)
-sample_df <- data.frame(E = numeric(), sample_diff = numeric(), actual_diff = numeric(), sex_prediction_accuracy = numeric())
-for (E in effect_sizes) {
-    # generate the fake males
-    fake_male_params <- generate_fake_male_params(E)
-    generate_fake_male_sample <- generate_generate_alligator_samples(fake_male_params)
-    
-    # samples
-    female_age <- runif(num_samples, 1, ALLIGATOR_MAX_LIFESPAN)
-    female_length <- generate_female_sample(female_age)
-    male_age <- runif(num_samples, 1, ALLIGATOR_MAX_LIFESPAN)
-    male_length <- generate_fake_male_sample(male_age)
-    combined_data <- data.frame(
-        age = c(female_age, male_age),
-        length = c(female_length, male_length),
-        sex = rep(c("F", "M"), each = num_samples)
-    )
-    combined_data <- subset(combined_data, length > 0)
-
-    population_fit <- generate_vb_curve_fit(combined_data)
-    population_params <- coef(population_fit)
-
-    prior_L <- c(population_params[['L']], 0.5)
-    prior_K <- c(population_params[['K']], 0.025)
-    prior_A <- c(population_params[['A']], 0.25)
-    prior_sigma <- c(sigma, 0.05)
-    
-    combined_data$predicted_sex <- generate_predicted_sex(combined_data, fit = population_fit)
-    male_data <- subset(combined_data, predicted_sex == "M")
-    female_data <- subset(combined_data, predicted_sex == "F")
-    sex_prediction_accuracy <- sum(combined_data$sex == combined_data$predicted_sex) / nrow(combined_data)
-
-    data <- list(
-            N_male = nrow(male_data),
-            age_male = male_data$age,
-            length_male = male_data$length,
-            N_female = nrow(female_data),
-            age_female = female_data$age,
-            length_female = female_data$length,
-            prior_L = prior_L,
-            prior_A = prior_A,
-            prior_K = prior_K,
-            prior_sigma = prior_sigma
-        )
-    model <- stan("vb_dimorphism_model.stan", data = data, iter = 8000)
-    samples <- extract(model)
-    sample_df <- rbind(
[…]

### 2024-02-12 paper/code/alligatorMethod.R

@@ -1,25 +1,0 @@
-source("functions.R")
-
-# generate the sample
-num_samples <- 1e3
-combined_data <- generate_combined_alligator_sample(generate_male_sample, generate_female_sample, num_samples)
-
-population_fit <- generate_vb_curve_fit(combined_data)
-population_params <- coef(population_fit)
-
-curve_ages <- seq(1, ALLIGATOR_MAX_LIFESPAN, length.out = 100)
-curve_lengths <- generalized_von_bertalanffy(curve_ages, L = population_params[['L']], A = population_params[['A']], K = population_params[['K']])
-curve_data <- data.frame(age = curve_ages, length = curve_lengths)
-
-p <- ggplot(combined_data, aes(age, length)) +
-    geom_point(aes(shape = sex, colour = sex)) +
-    geom_line(data = curve_data, mapping = aes(age, length), linewidth = 2) +
-    annotate('label', label = "Predicted Male", x = 25, y = 3.7, size = unit(8, 'pt'), fill = 'white', label.size = NA) +
-    annotate('label', label = "Predicted Female", x = 25, y = 1.2, size = unit(8, 'pt'), fill = 'white', label.size = NA) +
-    annotate('label', label = "Population Curve", x = 35, y = 2.8, size = unit(8, 'pt'), fill = 'white', label.size = NA) +
-    scale_colour_grey() +
-    scale_fill_grey() +
-    custom_theme() +
-    labs(x = "Age (years)", y = "Length (m)", title = "Alligator Population and Curve", colour = "Actual Sex", shape = "Actual Sex")
-ggsave("../images/alligatorMethod.png", plot = p,  width = 15, height = 8)
-print("Done")

### 2024-02-12 paper/code/alligatorSampleSize.R

@@ -1,82 +1,0 @@
-source("functions.R")
-
-# for reproducibility
-set.seed(2024)
-
-sample_sizes <- c(5, 10, 20, 50, 100)
-sample_df <- data.frame(sample_size = integer(), diff = numeric())
-for (sample_size in sample_sizes) {
-    male_ages <- runif(sample_size, 1, ALLIGATOR_MAX_LIFESPAN)
-    male_length <- generate_male_sample(male_ages)
-    female_ages <- runif(sample_size, 1, ALLIGATOR_MAX_LIFESPAN)
-    female_length <- generate_female_sample(female_ages)
-    combined_data <- data.frame(
-        age = c(male_ages, female_ages),
-        length = c(male_length, female_length),
-        sex = rep(c("M", "F"), each = sample_size)
-    )
-    population_fit <- generate_vb_curve_fit(combined_data)
-    population_params <- coef(population_fit)
-    prior_L <- c(population_params[['L']], 0.5)
-    prior_K <- c(population_params[['K']], 0.025)
-    prior_A <- c(population_params[['A']], 0.25)
-    prior_sigma <- c(sigma, 0.05)
-    combined_data$predicted_sex <- generate_predicted_sex(combined_data, fit = population_fit)
-    male_data <- subset(combined_data, predicted_sex == "M")
-    female_data <- subset(combined_data, predicted_sex == "F")
-
-    data <- list(
-            N_male = nrow(male_data),
-            age_male = male_data$age,
-            length_male = male_data$length,
-            N_female = nrow(female_data),
-            age_female = female_data$age,
-            length_female = female_data$length,
-            prior_L = prior_L,
-            prior_A = prior_A,
-            prior_K = prior_K,
-            prior_sigma = prior_sigma
-        )
-    model <- stan("vb_dimorphism_model.stan", data = data, iter = 8000)
-    samples <- extract(model)
-    sample_df <- rbind(
-        sample_df,
-        data.frame(sample_size = sample_size * 2, diff = samples[['diff']])
-    )
-}
-
-alpha <- 0.05
-summary_df <- data.frame(
-    sample_size = integer(),
-    mean = numeric(),
-    lower = numeric(),
-    upper = numeric()
-)
-
-for (sample_size in unique(sample_df$sample_size)) {
[…]

### 2024-02-12 paper/code/constants.R

@@ -1,14 +1,0 @@
-ALLIGATOR_MAX_LIFESPAN <- 50
-sigma = 0.25
-actual_male_params <- list(
-    L = 3.79,
-    A = 0.94,
-    K = 0.0695,
-    sigma = sigma
-)
-actual_female_params <- list(
-    L = 2.78,
-    A = 0.91,
-    K = 0.0926,
-    sigma = sigma
-)

### 2024-02-12 paper/code/dinosaurs.R

@@ -1,447 +1,0 @@
-source("functions.R")
-set.seed(2024)
-
-#### Maiasaura
-data <- read.csv('data/Maiasaura.csv')
-head(data)
-
-maiasaura <- data.frame(
-    age = data$Age..years. + data$Age.shift..years.,
-    mass = data$Fraction.multiplied.to.ROM.44770.body.mass..kg.
-)
-
-maiasaura_plot <- ggplot(maiasaura, aes(age, mass)) +
-    geom_point() +
-    labs(x = "Age (years)", y = "Mass (kg)", title = "Maiasaura peeblesorum") +
-    custom_theme()
-
-initial_maiasaura_params <- list(
-    L=2500,
-    k=0.5,
-    q=10
-)
-
-population_fit <- generate_logistic_curve_fit(maiasaura, initial_params = initial_maiasaura_params)
-population_params <- coef(population_fit)
-
-# generate the priors plot
-num_samples <- 1e3
-Ls <- rnorm(num_samples, population_params[['L']], sd = 500)
-ks <- rnorm(num_samples, population_params[['k']], sd = 0.0125)
-qs <- rnorm(num_samples, population_params[['q']], sd = 0.4)
-sigmas <- rnorm(num_samples, 200, 50)
-
-curve_data <- data.frame(age = numeric(), length = numeric())
-curve_ages <- seq(min(maiasaura$age), max(maiasaura$age), by = 0.5)
-for (i in 1:1e3) {
-    index <- sample(1:num_samples, size = 1)
-    L <- Ls[index]
-    k <- ks[index]
-    q <- qs[index]
-    sigma <- sigmas[index]
-
-    curve_mass_mean <- generalized_logistic(curve_ages, L = L, k = k, q = q)
-    curve_mass <- rnorm(length(curve_mass_mean), mean = curve_mass_mean, sd = sigma)
-    curve_data <- rbind(
-        curve_data,
-        data.frame(age = curve_ages, mass = curve_mass)
-    )
-}
-
-range_df <- data.frame(age = numeric(), lower = numeric(), upper = numeric())
-for (age in unique(curve_data$age)) {
-    relevant <- curve_data[abs(curve_data$age - age) < 0.1, ]
-    masses <- relevant$mass
-    lower <- quantile(masses, c(0.025))
-    upper <- quantile(masses, c(0.975))
-    range_df <- rbind(
-        range_df,
-        data.frame(
-            age = age,
-            lower = lower,
[…]

### 2024-02-12 paper/code/functions.R

@@ -1,118 +1,0 @@
-
-library(ggplot2)
-library(FSA) # for the vbStart function to find good parameters for the von Bertalanffy function
-library(minpack.lm) # a more robust version of nls for non-linear curve fitting to avoid problems with e.g. very small sample sizes
-library(rstan)
-
-options(mc.cores = parallel::detectCores())
-rstan_options(auto_write = TRUE)
-
-source("constants.R")
-
-custom_theme <- function() {
-  theme_minimal() +
-    theme(
-      panel.background = element_rect(fill = "white"),
-      panel.grid.major = element_line(color = alpha("black", 0.5), linetype = "dotted", linewidth = 0.5),
-      panel.grid.minor = element_blank(),
-      axis.text = element_text(size = 12),  # Adjust the font size of axis labels
-      axis.title = element_text(size = 16),  # Adjust the font size of axis titles
-      plot.title = element_text(size = 20, hjust = 0.5),  # Adjust the font size and center the plot title
-      plot.subtitle = element_text(size = 16, hjust = 0.5)  # Adjust the font size and center the plot subtitle
-    )
-}
-
-paper_colours <- function() {
-    scale_colour_grey() +
-    scale_fill_grey()
-}
-
-poster_colours <- function() {
-
-}
-
-generalized_von_bertalanffy <- function(age, L, A, K) {
-    L * (1 - A * exp(-K * age))
-}
-
-generalized_logistic <- function(age, L, q, k) {
-    L / (1 + exp(q + k * age))
-}
-
-generate_initial_vb_params <- function(df, debug = FALSE) {
-    initial_params_raw <- tryCatch({vbStarts(df$length ~ df$age)},
-        error = function(e) {
-            if (debug) {
-                cat("Error getting initial von Bertalanffy parameters for data", conditionMessage(e))
-            }
-            NULL
-        }
-    )
-
-    if (is.null(initial_params_raw)) return(NULL)
-
-    # now convert to my parameterization
-    # I use y = Linf * (1 - A e ^ (-Kt) )
-    # they use y = Linf * (1 - e^(-K (t - t0)))
-    # -> A = e^K t0
-    initial_params <- list(
-        L = initial_params_raw$Linf,
-        K = initial_params_raw$K,
-        A = exp(initial_params_raw$K * initial_params_raw$t0)
-    )
-    initial_params
-}
-
-generate_vb_curve_fit <- function(data) {
[…]

### 2024-02-12 paperAndPoster/code/alligatorEffectSize.R

@@ -1,0 +1,111 @@
+source("functions.R")
+
+set.seed(2024)
+alpha <- 0.05
+num_samples <- 1e3 / 2
+effect_sizes <- seq(0, 2, length.out = 10)
+sample_df <- data.frame(E = numeric(), sample_diff = numeric(), actual_diff = numeric(), sex_prediction_accuracy = numeric())
+for (E in effect_sizes) {
+    # generate the fake males
+    fake_male_params <- generate_fake_male_params(E)
+    generate_fake_male_sample <- generate_generate_alligator_samples(fake_male_params)
+    
+    # samples
+    female_age <- runif(num_samples, 1, ALLIGATOR_MAX_LIFESPAN)
+    female_length <- generate_female_sample(female_age)
+    male_age <- runif(num_samples, 1, ALLIGATOR_MAX_LIFESPAN)
+    male_length <- generate_fake_male_sample(male_age)
+    combined_data <- data.frame(
+        age = c(female_age, male_age),
+        length = c(female_length, male_length),
+        sex = rep(c("F", "M"), each = num_samples)
+    )
+    combined_data <- subset(combined_data, length > 0)
+
+    population_fit <- generate_vb_curve_fit(combined_data)
+    population_params <- coef(population_fit)
+
+    prior_L <- c(population_params[['L']], 0.5)
+    prior_K <- c(population_params[['K']], 0.025)
+    prior_A <- c(population_params[['A']], 0.25)
+    prior_sigma <- c(sigma, 0.05)
+    
+    combined_data$predicted_sex <- generate_predicted_sex(combined_data, fit = population_fit)
+    male_data <- subset(combined_data, predicted_sex == "M")
+    female_data <- subset(combined_data, predicted_sex == "F")
+    sex_prediction_accuracy <- sum(combined_data$sex == combined_data$predicted_sex) / nrow(combined_data)
+
+    data <- list(
+            N_male = nrow(male_data),
+            age_male = male_data$age,
+            length_male = male_data$length,
+            N_female = nrow(female_data),
+            age_female = female_data$age,
+            length_female = female_data$length,
+            prior_L = prior_L,
+            prior_A = prior_A,
+            prior_K = prior_K,
+            prior_sigma = prior_sigma
+        )
+    model <- stan("vb_dimorphism_model.stan", data = data, iter = 8000)
+    samples <- extract(model)
+    sample_df <- rbind(
[…]

### 2024-02-12 paperAndPoster/code/alligatorMethod.R

@@ -1,0 +1,25 @@
+source("functions.R")
+
+# generate the sample
+num_samples <- 1e3
+combined_data <- generate_combined_alligator_sample(generate_male_sample, generate_female_sample, num_samples)
+
+population_fit <- generate_vb_curve_fit(combined_data)
+population_params <- coef(population_fit)
+
+curve_ages <- seq(1, ALLIGATOR_MAX_LIFESPAN, length.out = 100)
+curve_lengths <- generalized_von_bertalanffy(curve_ages, L = population_params[['L']], A = population_params[['A']], K = population_params[['K']])
+curve_data <- data.frame(age = curve_ages, length = curve_lengths)
+
+p <- ggplot(combined_data, aes(age, length)) +
+    geom_point(aes(shape = sex, colour = sex)) +
+    geom_line(data = curve_data, mapping = aes(age, length), linewidth = 2) +
+    annotate('label', label = "Predicted Male", x = 25, y = 3.7, size = unit(8, 'pt'), fill = 'white', label.size = NA) +
+    annotate('label', label = "Predicted Female", x = 25, y = 1.2, size = unit(8, 'pt'), fill = 'white', label.size = NA) +
+    annotate('label', label = "Population Curve", x = 35, y = 2.8, size = unit(8, 'pt'), fill = 'white', label.size = NA) +
+    scale_colour_grey() +
+    scale_fill_grey() +
+    custom_theme() +
+    labs(x = "Age (years)", y = "Length (m)", title = "Alligator Population and Curve", colour = "Actual Sex", shape = "Actual Sex")
+ggsave("../images/alligatorMethod.png", plot = p,  width = 15, height = 8)
+print("Done")

### 2024-02-12 paperAndPoster/code/alligatorSampleSize.R

@@ -1,0 +1,82 @@
+source("functions.R")
+
+# for reproducibility
+set.seed(2024)
+
+sample_sizes <- c(5, 10, 20, 50, 100)
+sample_df <- data.frame(sample_size = integer(), diff = numeric())
+for (sample_size in sample_sizes) {
+    male_ages <- runif(sample_size, 1, ALLIGATOR_MAX_LIFESPAN)
+    male_length <- generate_male_sample(male_ages)
+    female_ages <- runif(sample_size, 1, ALLIGATOR_MAX_LIFESPAN)
+    female_length <- generate_female_sample(female_ages)
+    combined_data <- data.frame(
+        age = c(male_ages, female_ages),
+        length = c(male_length, female_length),
+        sex = rep(c("M", "F"), each = sample_size)
+    )
+    population_fit <- generate_vb_curve_fit(combined_data)
+    population_params <- coef(population_fit)
+    prior_L <- c(population_params[['L']], 0.5)
+    prior_K <- c(population_params[['K']], 0.025)
+    prior_A <- c(population_params[['A']], 0.25)
+    prior_sigma <- c(sigma, 0.05)
+    combined_data$predicted_sex <- generate_predicted_sex(combined_data, fit = population_fit)
+    male_data <- subset(combined_data, predicted_sex == "M")
+    female_data <- subset(combined_data, predicted_sex == "F")
+
+    data <- list(
+            N_male = nrow(male_data),
+            age_male = male_data$age,
+            length_male = male_data$length,
+            N_female = nrow(female_data),
+            age_female = female_data$age,
+            length_female = female_data$length,
+            prior_L = prior_L,
+            prior_A = prior_A,
+            prior_K = prior_K,
+            prior_sigma = prior_sigma
+        )
+    model <- stan("vb_dimorphism_model.stan", data = data, iter = 8000)
+    samples <- extract(model)
+    sample_df <- rbind(
+        sample_df,
+        data.frame(sample_size = sample_size * 2, diff = samples[['diff']])
+    )
+}
+
+alpha <- 0.05
+summary_df <- data.frame(
+    sample_size = integer(),
+    mean = numeric(),
+    lower = numeric(),
+    upper = numeric()
+)
+
+for (sample_size in unique(sample_df$sample_size)) {
[…]

### 2024-02-12 paperAndPoster/code/constants.R

@@ -1,0 +1,14 @@
+ALLIGATOR_MAX_LIFESPAN <- 50
+sigma = 0.25
+actual_male_params <- list(
+    L = 3.79,
+    A = 0.94,
+    K = 0.0695,
+    sigma = sigma
+)
+actual_female_params <- list(
+    L = 2.78,
+    A = 0.91,
+    K = 0.0926,
+    sigma = sigma
+)

### 2024-02-13 paperAndPoster/paper.tex
feat: updated graphs with default save options

--- 2024-02-11 paper/paper.tex
@@
 \usepackage{booktabs}
+\usepackage{xurl}
 
-\title{Using Bayesian Regression to Quantify Sexual Dimorphism in Extinct Taxa}
+\title{Using Bayesian Regression to Quantify Sexual Dimorphism in Dinosaurs}
 \author{Eric Campbell}
@@
 \section{Methods}
+Bayesian regression is quite different from classical regression.
+To estimate a parameter, there needs to be a \emph{prior} representing the information that you have before seeing the data.
+You can then calculate the \emph{likelihood} of the data that you observed for the different parameter values.
+The optimal combination of the prior and the likelihood is given by Bayes' Theorem and is termed the \emph{posterior}.
+In general, the result of a Bayesian analysis will be a probability distribution, not a single number \parencite{mcelreathStatisticalRethinkingBayesian2020}.
+An illustration of this method is shown in Figure \ref{fig:bayesianExplanation}.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width = \textwidth]{images/bayesianExample.png}
+	\caption{To estimate human height, we start with what we know before seeing any data --- the \emph{prior}.
+Then a sample of heights is collected and the \emph{likelihood} of that sample for each of the parameter values is calculated.
+The combination of those, our final belief about the value of the parameter, is the \emph{posterior} distribution.}
+	\label{fig:bayesianExplanation}
+\end{figure}
+
 The modification to the method in \cite{saittaEffectSizeStatistical2020} is presented below.
@@
 K_{ m/f } &\sim \normal{\text{population K}}{0.05} \\
-\sigma &= 0.25 \\
+\sigma &\sim \normal{0.25}{0.05} \\
 \end{align*}
@@
 
-Despite these advantages, there remain many area in which this method could be improved.
+Despite these advantages, there remain many areas in which this method could be improved.
 The most critical, as noted in \cite{saittaEffectSizeStatistical2020}, is sex determination.
@@
 \printbibliography[title=Bibliography]
+For all data and code used here, along with additional analyses, see \url{https://github.com/EricRobertCampbell/aps-2024-poster-sexual-dimorphism}.
+
 \end{document}

### 2024-02-13 paperAndPoster/code/alligatorEffectSize.R

@@ -68,8 +68,9 @@ p <- ggplot(sample_df, aes(error, group = E, colour = E)) +
     ) +
     labs(x = "Error (Predicted - Actual)", y = "Density", title = "Effect Size on Dimorphism Error", colour = "Effect Size") +
     scale_y_continuous(labels = NULL) +
-    custom_theme()
-ggsave("../images/alligatorEffectSize.png", plot = p, width = 15, height = 8)
+    custom_theme() +
+    theme(legend.position = c(0.2, 0.8), legend.background = element_rect(fill = 'white'))
+ggsave_with_defaults(generate_filename("alligatorEffectSize.png"), plot = p)
 
 # now the error by sex prediction error
 error_by_error_df <- data.frame(
@@ -107,5 +108,6 @@ p <- ggplot(error_by_error_df, aes(sex_prediction_accuracy, mean_error, colour =
     ) +
     scale_x_continuous(labels = scales::percent) +
     labs(x = "Sex Prediction Accuracy", y = "Error (Predicted - Actual)", colour = "Effect Size", title = "Relationship Between Dimorphism Error and Sex Prediction Accuracy") +
-    custom_theme()
-ggsave('../images/alligatorSexPredictionAccuracyDimorphismError.png', plot = p, width = 15, height = 8)
+    custom_theme() +
+    theme(legend.position = c(0.9, 0.8), legend.background = element_rect(fill = 'white'))
+ggsave_with_defaults(generate_filename('alligatorSexPredictionAccuracyDimorphismError.png'), plot = p)

### 2024-02-13 paperAndPoster/code/alligatorMethod.R

@@ -20,6 +20,6 @@ p <- ggplot(combined_data, aes(age, length)) +
     scale_colour_grey() +
     scale_fill_grey() +
     custom_theme() +
-    labs(x = "Age (years)", y = "Length (m)", title = "Alligator Population and Curve", colour = "Actual Sex", shape = "Actual Sex")
-ggsave("../images/alligatorMethod.png", plot = p,  width = 15, height = 8)
-print("Done")
+    labs(x = "Age (years)", y = "Length (m)", title = "Alligator Population and Curve", colour = "Actual Sex", shape = "Actual Sex") +
+    theme(legend.position = c(0.85, 0.25), legend.background = element_rect(fill = 'white'))
+ggsave_with_defaults(generate_filename("alligatorMethod.png"), plot = p)

### 2024-02-13 paperAndPoster/code/alligatorSampleSize.R

@@ -79,4 +79,4 @@ p <- ggplot(summary_df, aes(sample_size, mean)) +
     annotate('label', label = "Actual Level", x = 4.5, y = 0.7, size = unit(8, 'pt'), fill = 'white', label.size = NA) +
     labs(x = "Total Sample Size", y = "Dimorphism Level (m)", title = "Dimorphism Level (Mean and 95% Credible Interval) and Sample Size") +
     custom_theme()
-ggsave("../images/alligatorSampleSize.png", plot = p, width = 15, height = 8)
+ggsave_with_defaults(generate_filename("alligatorSampleSize.png"), plot = p)

### 2024-02-13 paperAndPoster/code/bayesianExample.R

@@ -1,0 +1,33 @@
+source("functions.R")
+
+set.seed(2024)
+
+prior_h <- c(160, 10)
+actual_h <- c(176, 7)
+
+sample <- rnorm(10, actual_h[1], actual_h[2])
+
+heights <- seq(140, 200, length.out = 1000)
+prior_likelihood <- dnorm(heights, prior_h[1], prior_h[2])
+likelihood_likelihood <- sapply(heights, function(h) sum(dnorm(sample, h, actual_h[2])))
+posterior <- prior_likelihood * likelihood_likelihood
+
+prior_likelihood <- prior_likelihood / sum(prior_likelihood)
+likelihood_likelihood <- likelihood_likelihood / sum(likelihood_likelihood)
+posterior <- posterior / sum(posterior)
+
+df <- data.frame(
+    height = rep(heights, 3),
+    density = c(prior_likelihood, likelihood_likelihood, posterior),
+    type = rep(c("Prior", "Likelihood", "Posterior"), each = length(heights))
+)
+
+p <- ggplot(df, aes(height, density, group = type, colour = type)) +
+    geom_line(linewidth = 2) +
+    custom_theme() +
+    labs(x = "Height (cm)", y = "Density", colour = "Type") +
+    scale_y_continuous(labels = NULL) +
+    scale_colour_grey() +
+    theme(legend.position = c(0.8, 0.8), legend.background = element_rect(fill = 'white'))
+
+ggsave_with_defaults(generate_filename("bayesianExample.png"), plot = p)

### 2024-02-13 paperAndPoster/code/dinosaurs.R

@@ -69,7 +69,7 @@ p <- ggplot() +
     labs(x = "Age (years)", y = "Mass (kg)", title = "Prior 95% Quantiles") +
     custom_theme()
 
-ggsave("../images/maiasauraPrior.png", plot = p, width = 15, height = 8)
+ggsave_with_defaults(generate_filename("maiasauraPrior.png"), plot = p)
 
 # now do the regression
 maiasaura$residual <- resid(population_fit)
@@ -122,15 +122,17 @@ for (i in 1:100) {
         geom_line(data = data.frame(age = curve_ages, mass = curve_mass_large, sex = "L"), mapping = aes(age, mass, colour = sex), alpha = 0.1)
 
 }
-p <- p + labs(title = "Maiasaura peeblesorum Data and Posterior Growth Curves")
-ggsave('../images/maiasauraPosterior.png', plot = p, width = 15, height = 8)
+p <- p +
+    labs(title = "Maiasaura peeblesorum Data and Posterior Growth Curves") +
+    theme(legend.position = c(0.7, 0.3), legend.background = element_rect(fill = 'white'))
+ggsave_with_defaults(generate_filename('maiasauraPosterior.png'), plot = p)
 
 # actual amount of dimorphism
 p <- ggplot(data.frame(x = maiasaura_samples[['difference']]), aes(x)) +
     geom_density(aes(y = after_stat(density))) +
     labs(x = expression(L[l] - L[s]), y = "Density", title = "Posterior Distribution for Maiasaura Sexual Dimorphism") +
     custom_theme()
-ggsave('../images/maiasauraDimorphism.png', plot = p, width = 15, height = 8)
+ggsave_with_defaults(generate_filename('maiasauraDimorphism.png'), plot = p)
 
 
 
@@ -205,7 +207,7 @@ p <- ggplot() +
     labs(x = "Age (years)", y = "Mass (kg)", title = "Prior 95% Quantiles") +
     custom_theme()
 
-ggsave("../images/psittacosaurusPrior.png", plot = p, width = 15, height = 8)
+ggsave_with_defaults(generate_filename("psittacosaurusPrior.png"), plot = p)
 
 # now fit the psittacosaurus data
 psittacosaurus$residual <- resid(fit.population)
@@ -259,14 +261,16 @@ for (i in 1:100) {
[…]

### 2024-02-13 paperAndPoster/code/functions.R

@@ -116,3 +116,17 @@ generate_fake_male_params <- function(E) {
         sigma = actual_female_params[['sigma']] + E * (actual_male_params[['sigma']] - actual_female_params[['sigma']])
     )
 }
+
+ggsave_with_defaults <- function(filename, plot, width = 15, height = 8, dpi = 600, ...) {
+  ggsave(
+    filename = filename,
+    plot = plot,
+    width = width,
+    height = height,
+    dpi = dpi,
+    ...
+  )
+  sprintf("Done saving %s", filename)
+}
+
+generate_filename <- function(name) sprintf("../images/%s", name)

### 2024-02-15 paperAndPoster/paper.tex
fix: minor edits to pdf and docx of paper

@@
 \title{Using Bayesian Regression to Quantify Sexual Dimorphism in Dinosaurs}
-\author{Eric Campbell}
+\author{Eric Campbell \\ \texttt{eric.robert.campbell@gmail.com}}
+\date{}
 \begin{document}
@@
 \begin{align*}
-\text{Length}_{ m / f } &\sim \mathcal{N}\left(\mu_{ m / f }, \sigma\right) \\
+\text{Length}_{ m / f } &\sim \mathcal{N}\left(\mu_{ m / f }, \sigma_{m/f}\right) \\
 \mu_m &= 3.79 * \left(1 - 0.94e^{-0.0695 \ast \text{age}}\right) \\
 \mu_f &= 2.78 * \left(1 - 0.91e^{-0.0926 \ast \text{age}}\right) \\
-\sigma &= 0.25
+\sigma_{m/f} &= 0.25
 \end{align*}
@@
 K_{ m/f } &\sim \normal{\text{population K}}{0.05} \\
-\sigma &\sim \normal{0.25}{0.05} \\
+\sigma_{m/f} &\sim \normal{0.25}{0.05} \\
 \end{align*}
@@
 
-As shown above, the modification of the method in \cite{saittaEffectSizeStatistical2020} using Bayesian regression to calculate the posterior distributions for sex-specific growth curves and the level of sexual dimorphism is generally reliable and useful way to quantify dimorphism in extinct populations.
-While it shares some weakness with with the original method, it also has several notable advantages.
+As shown above, the modification of the method in \cite{saittaEffectSizeStatistical2020} using Bayesian regression to calculate the posterior distributions for sex-specific growth curves and the level of sexual dimorphism is a generally reliable and useful way to quantify dimorphism in extinct populations.
+While it shares some weakness with the original method, it also has several notable advantages.
 One is that by carrying uncertainty through all parts of modelling, the final result contains more information about the process \parencite{mcelreathStatisticalRethinkingBayesian2020}.

### 2024-02-15 paperAndPoster/poster.tex
fix: minor edits to pdf and docx of paper
trouble with bibliography

@@
-\documentclass[a0paper, landscape]{tikzposter} % See Section 3
-\title{Title} \institute{Inst} % See Section 4.1
-\author{Auth} \titlegraphic{Logo}
+\documentclass[landscape]{tikzposter} % See Section 3
+\input{common.tex}
+
+\title{\actualTitle} % See Section 4.1
+\author{Eric Campbell \\ \texttt{eric.robert.campbell@gmail.com}} 
 \usetheme{Basic} % See Section 5
@@
 \maketitle % See Section 4.1
-\block{BlocktitleA}{Blocktext} % See Section 4.2
+\block{Abstract}{Put abstract here} % See Section 4.2
 \begin{columns} % See Section 4.4
-\column{0.3} % See Section 4.4
+\column{0.333333333} % See Section 4.4
 \block{BlocktitleB}{Blocktext}
-\column{0.7}
+
+\column{0.333333333}
 \block{BlocktitleC}{Blocktext}
+
+\column{0.333333333}
+\block{Results}{Put Results Here}
+\block{Next Steps}{Ideas for next steps here}
+\block{Bibliography}{
+    % \input{paper.bbl}
+
+    For all data and code used here, along with additional analyses, see \url{https://github.com/EricRobertCampbell/aps-2024-poster-sexual-dimorphism}.
+}
 \note{Notetext} % See Section 4.3
+
 \end{columns}

### 2024-02-16 paperAndPoster/paper.tex
trouble with bibliography
feat: inserted paper bibliography into poster

@@
 \usepackage{float}
-\usepackage{amsmath}
 \usepackage{tabularx}
@@
 \usepackage{booktabs}
-\usepackage{xurl}
+\input{common.tex}
 
-\title{Using Bayesian Regression to Quantify Sexual Dimorphism in Dinosaurs}
+\title{\actualTitle}
 \author{Eric Campbell \\ \texttt{eric.robert.campbell@gmail.com}}
@@
 \maketitle
-
-\newcommand{\species}[1]{\textit{#1}}
-\newcommand{\tyran}{\species{Tyrannosaurus rex}{}}
-\newcommand{\psit}{\species{Psittacosurus lujiatunensis}{}}
-\newcommand{\maia}{\species{Maiasaura peeblesorum}{}}
-\newcommand{\normal}[2]{\ensuremath{\mathcal{N}\left(#1, #2\right)}}
 
@@
 \begin{align*}
-\text{Length}_{m/f,i} &\sim \normal{\mu_{m/f, i}}{\sigma} \\
-\mu_{m/f, i} &= \text{von Betlananffy}(\text{age}_i, L_{ m/f }, A_{ m/f }, K_{ m/f }) \\
+\text{Length}_{m/f,i} &\sim \normal{\mu_{m/f, i}}{\sigma_{m / f}} \\
+\mu_{m/f, i} &= \text{von Bertalanffy}(\text{age}_i, L_{ m/f }, A_{ m/f }, K_{ m/f }) \\
 L_{ m/f } &\sim \normal{\text{population L}}{0.5} \\

### 2024-02-18 paperAndPoster/paper.tex
feat: first pass at poster

@@
 \usepackage{float}
-\usepackage{tabularx}
 \usepackage{siunitx}
@@
 \usepackage{subcaption}
-\usepackage{booktabs}
 \input{common.tex}
@@
 However, each of these has their weaknesses.
-The use of $t$ tests (for differences in the mean) or Hartigans' dip test (for unimodality) can suffer from low statistical power \parencite{mallonRecognizingSexualDimorphism2017} and in the case of $t$ tests a further difficulty is the prolonged growth period of most dinosaurs \parencite{honeProtractedGrowthImpedes2017}.
+The use of $t$ tests (for differences in the mean) or Hartigans' dip test (for unimodality) \parencite{hartiganDipTestUnimodality1985} can suffer from low statistical power \parencite{mallonRecognizingSexualDimorphism2017} and in the case of $t$ tests a further difficulty is the prolonged growth period of most dinosaurs \parencite{honeProtractedGrowthImpedes2017}.
 As a result, positive results for dimorphism in dinosaurs are rare.

### 2024-02-18 paperAndPoster/poster.tex
feat: inserted paper bibliography into poster
feat: first pass at poster

@@
-\documentclass[landscape]{tikzposter} % See Section 3
+\documentclass[
+  landscape,
+  a0paper,
+  20pt,
+  margin=0mm,
+  innermargin=10mm,
+  blockverticalspace=0mm,
+  colspace=5mm,
+]{tikzposter} % See Section 3
+\usepackage{xcolor}
+\usepackage[style=authoryear-comp, locallabelwidth]{biblatex}
+\addbibresource{bibliography.bib}
 \input{common.tex}
+
+\renewcommand*{\bibfont}{\tiny}
 
@@
 \author{Eric Campbell \\ \texttt{eric.robert.campbell@gmail.com}} 
-\usetheme{Basic} % See Section 5
+\institute{Calefy Inc.}
+\settitle{ \centering \vbox{
+\@titlegraphic \\[\TP@titlegraphictotitledistance] \centering
+\color{titlefgcolor} {\bfseries \Huge \sc \@title \par}
+\vspace*{1em}
+{\huge \@author \par} \vspace*{1em} {\LARGE \@institute} \vspace*{1em}
+
+}}
+\usetheme{Simple} % See Section 5
 
 \begin{document}
-\maketitle % See Section 4.1
-\block{Abstract}{Put abstract here} % See Section 4.2
+\maketitle[
+    width = 0.8\textwidth,
+    titletotopverticalspace = 5mm,
+    titletoblockverticalspace = 5mm,
+  ] % See Section 4.1
+\block{Abstract}{While sexual dimorphism is common in extant taxa, detection in extinct taxa is made challenging by difficulties in determining the sex and size of organisms.
+Existing methods suffer from a lack of statistical power, making positive identification of dimorphism difficult.
+Herein is outline an modification to a method from \cite{saittaEffectSizeStatistical2020} which constructs sex-specific growth curves to determine sexual size dimorphism, but using Bayesian regression to construct the curves rather than standard non-linear regression.
+The method is shown to be robust and reliable, with the additional benefit of incorporating prior information to constrain dimorphism to biologically plausible levels.} % See Section 4.2
 \begin{columns} % See Section 4.4
 \column{0.333333333} % See Section 4.4
-\block{BlocktitleB}{Blocktext}
+\block{Introduction}{
+  \begin{itemize}
+    \item Sexual dimorphism is common in extant taxa, but positive examples in dinosaurs are rare
+    \item Determining sex and size of an extinct organism is difficult
+    \item Existing methods suffer from low statistical power and can be confounded by e.g. juveniles
+    \item Method in \cite{saittaEffectSizeStatistical2020}: construct growth curves for predicted male and females separately to measure dimorphism
+    \item Can suffer from lack of numerical convergence and implausible predictions (e.g. negative masses), particularly for small sample sizes
+    \item Proposed modification: use Bayesian regression to estimte growth curves
+  \end{itemize}
+}
+\block{Method}{
+  \begin{enumerate}
+        \item Gather data: age (or a correlate) and character of interest (e.g. length)
+        \item Fit growth curve to population as a whole 
+        \item Predict sex by assigning all samples above the population curve to one sex and all below to the other. 
+        \item \textcolor{red}{Fit separate growth curves to each predicted sex} $\to$ Create a posterior distribution for sex-specific parameters (Bayesian regression)
+        \item \textcolor{red}{Calculate maximum likelihood level of dimorphism} $\to$ Calculate posterior distribution for dimorphism
+  \end{enumerate}
+  \begin{tikzfigure}[Simulated Alligator Populations \& Method]
+    \includegraphics[width = 0.9\colwidth]{images/alligatorMethod-poster.png}
+  \end{tikzfigure}
+For all data and code used here, along with additional analyses, see \url{https://github.com/EricRobertCampbell/aps-2024-poster-sexual-dimorphism}.
+}
 
 \column{0.333333333}
-\block{BlocktitleC}{Blocktext}
+\block{Verification}{
+  Bayes' Theorem:
+  \[
+    \overbrace{P\left(\text{parameter value}|\text{data}\right)}^{\text{Posterior}} \propto \overbrace{P\left( \text{parameter value} \right)}^{\text{Prior}} \ast \overbrace{P \left( \text{data} | \text{parameter value}\right)}^{\text{Likelihood}}
+  \]
+
+    \begin{minipage}[t]{0.45\colwidth}
+      \begin{tikzfigure}[Bayesian parameter estimation]
+        \centering
+        \includegraphics[width = \textwidth]{images/bayesianExample-poster.png}
+        \label{fig:bayesianExplanation}
+      \end{tikzfigure}
+    \end{minipage}
+    \begin{minipage}[t]{0.45\colwidth}
+      \begin{itemize}
+          \item To estimate mean human height, start with what we know about the height before seeing any data --- the \emph{prior}
+          \item A sample of heights is collected and the \emph{likelihood} of that sample for each of the potential mean heights is calculated
+          \item Combination of those, our final belief about the value of the mean height, is the \emph{posterior} distribution
+      \end{itemize}
+    \end{minipage}
+  \begin{itemize}
+    \item American alligator (\species{Alligator mississippiensis}) growth parameters from \cite{wilkinsonGrowthRatesAmerican1997} (von Bertalanffy growth curve), but with constant standard deviation
+
+    \begin{minipage}[t]{0.45\colwidth}
+    \section*{Simulated}
+    \begin{align*}
+    \text{Length}_{ m / f } &\sim \mathcal{N}\left(\mu_{ m / f }, \sigma_{m/f}\right) \\
+    \mu_m &= 3.79 * \left(1 - 0.94e^{-0.0695 \ast \text{age}}\right) \\
+    \mu_f &= 2.78 * \left(1 - 0.91e^{-0.0926 \ast \text{age}}\right) \\
+    \sigma_{m/f} &= 0.25
+    \end{align*}
+  \end{minipage}
+  \begin{minipage}[t]{0.45\colwidth}
+    \section*{Model}
+    \begin{align*}
+    \text{Length}_{m/f,i} &\sim \normal{\mu_{m/f, i}}{\sigma_{m / f}} \\
+    \mu_{m/f, i} &= \text{von Bertalanffy}(\text{age}_i, \\
+                & L_{ m/f }, A_{ m/f }, K_{ m/f }) \\
+    L_{ m/f } &\sim \normal{\text{population L}}{0.5} \\
+    A_{ m/f } &\sim \normal{\text{population A}}{0.025} \\
+    K_{ m/f } &\sim \normal{\text{population K}}{0.05} \\
+    \sigma_{m/f} &\sim \normal{0.25}{0.05} \\
+    \end{align*}
+  \end{minipage}
+    \item Bayesian model with wide priors centred around the population-level curve values was used to recover the values \parencite{rCore, rstan}.
+
+  \end{itemize}
+    \begin{tikzfigure}[Verification results]
+      \includegraphics[width = 0.4\colwidth]{images/alligatorSampleSize-poster.png}
+      \includegraphics[width = 0.4\colwidth]{images/alligatorEffectSize-poster.png}
+
+      \includegraphics[width = 0.45\colwidth]{images/alligatorSexPredictionAccuracyDimorphismError-poster.png}
+    \end{tikzfigure}
+}
 
 \column{0.333333333}
-\block{Results}{Put Results Here}
-\block{Next Steps}{Ideas for next steps here}
-\block{Bibliography}{
-    % \input{paper.bbl}
+\block{Results}{
+  \begin{itemize}
+    \item \maia{}, \psit{}, and \tyran{}
+    \item Logistic curve with constant standard deviation was used for all species
+\[
+\text{logistic}(\text{age}, L, q, k) = \frac{L}{1 + e^{q+k \ast \text{age}}}
+  \]
+  \end{itemize}
+\begin{tikzfigure}[Posterior distribution and data]
+  \centering
+  \begin{minipage}[b]{0.3\colwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/maiasauraPosterior-poster.png}
+  \end{minipage}
+  \begin{minipage}[b]{0.3\colwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/psittacosaurusPosterior-poster.png}
+  \end{minipage}
+  \begin{minipage}[b]{0.3\colwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/tyrannosaurPosterior-poster.png}
+  \end{minipage}
+\end{tikzfigure}
 
-    For all data and code used here, along with additional analyses, see \url{https://github.com/EricRobertCampbell/aps-2024-poster-sexual-dimorphism}.
+\begin{tikzfigure}[Posterior relative dimorphism]
+  \centering
+  \includegraphics[width=0.9\colwidth]{images/combinedDimorphism-poster.png}
+\end{tikzfigure}
+  \begin{itemize}
+    \item Strong evidence for \maia{} (35\% -- 62\%), weak evidence for \psit{} (-2\% -- 31\%), and moderate evidence against \tyran{} (-7\% -- 13\%) dimorphism.
+    \item Benefits: incorporation of uncertainty and prior knowledge (constrain curve to be biologically feasible)
+  \end{itemize}
 }
-\note{Notetext} % See Section 4.3
+\block{Next Steps}{
+  \begin{itemize}
+    \item Incorporate measurement uncertainty (age, size) into the model
+    \item Improve sex prediction (clustering algorithms, incorporate additional features)
+    \item Use of mixture models to avoid assuming dimorphism
+  \end{itemize}
+}
+% \block{Bibliography}{
+%   \nocite{saittaEffectSizeStatistical2020}
+%   \nocite{brusatte2012}
+%   \nocite{mallonRecognizingSexualDimorphism2017}
+%   \nocite{honeProtractedGrowthImpedes2017}
+%   \nocite{wilkinsonGrowthRatesAmerican1997}
+%   \nocite{mcelreathStatisticalRethinkingBayesian2020}
+%   \nocite{rCore, rstan}
+%   % \nocite{rstan}
+%   \nocite{woodwardMaiasauraModelOrganism2015}
+%   \nocite{ericksonFlawedAnalysisResponse2015}
+%   \nocite{ericksonGigantismComparativeLifehistory2004}
+%   \nocite{hornerAgeGrowthDynamics2004}
+%   \nocite{leeSexualMaturityGrowing2008}
+%   \nocite{hartiganDipTestUnimodality1985}
+%     \begin{minipage}{\linewidth}
+%         \begin{center}\mbox{}\vspace{0pt}
+%             \printbibliography[heading=none]
+%         \end{center}
+%         \vspace{\baselineskip}
+%     \end{minipage}
+
+%     For all data and code used here, along with additional analyses, see \url{https://github.com/EricRobertCampbell/aps-2024-poster-sexual-dimorphism}.
+% }
 

### 2024-02-18 paperAndPoster/code/alligatorEffectSize.R

@@ -70,7 +70,10 @@ p <- ggplot(sample_df, aes(error, group = E, colour = E)) +
     scale_y_continuous(labels = NULL) +
     custom_theme() +
     theme(legend.position = c(0.2, 0.8), legend.background = element_rect(fill = 'white'))
-ggsave_with_defaults(generate_filename("alligatorEffectSize.png"), plot = p)
+paper_image <- p
+poster_image <- p
+ggsave_with_defaults(generate_filename("alligatorEffectSize.png"), plot = paper_image)
+ggsave_with_defaults(generate_filename("alligatorEffectSize-poster.png"), plot = poster_image)
 
 # now the error by sex prediction error
 error_by_error_df <- data.frame(
@@ -110,4 +113,7 @@ p <- ggplot(error_by_error_df, aes(sex_prediction_accuracy, mean_error, colour =
     labs(x = "Sex Prediction Accuracy", y = "Error (Predicted - Actual)", colour = "Effect Size", title = "Relationship Between Dimorphism Error and Sex Prediction Accuracy") +
     custom_theme() +
     theme(legend.position = c(0.9, 0.8), legend.background = element_rect(fill = 'white'))
-ggsave_with_defaults(generate_filename('alligatorSexPredictionAccuracyDimorphismError.png'), plot = p)
+paper_image <- p
+poster_image <- p
+ggsave_with_defaults(generate_filename('alligatorSexPredictionAccuracyDimorphismError.png'), plot = paper_image)
+ggsave_with_defaults(generate_filename('alligatorSexPredictionAccuracyDimorphismError-poster.png'), plot = poster_image)

### 2024-02-18 paperAndPoster/code/alligatorMethod.R

@@ -22,4 +22,8 @@ p <- ggplot(combined_data, aes(age, length)) +
     custom_theme() +
     labs(x = "Age (years)", y = "Length (m)", title = "Alligator Population and Curve", colour = "Actual Sex", shape = "Actual Sex") +
     theme(legend.position = c(0.85, 0.25), legend.background = element_rect(fill = 'white'))
-ggsave_with_defaults(generate_filename("alligatorMethod.png"), plot = p)
+
+paper_image <- p
+poster_image <- p
+ggsave_with_defaults(generate_filename("alligatorMethod.png"), plot = paper_image)
+ggsave_with_defaults(generate_filename("alligatorMethod-poster.png"), plot = poster_image)

### 2024-02-18 paperAndPoster/code/alligatorSampleSize.R

@@ -79,4 +79,8 @@ p <- ggplot(summary_df, aes(sample_size, mean)) +
     annotate('label', label = "Actual Level", x = 4.5, y = 0.7, size = unit(8, 'pt'), fill = 'white', label.size = NA) +
     labs(x = "Total Sample Size", y = "Dimorphism Level (m)", title = "Dimorphism Level (Mean and 95% Credible Interval) and Sample Size") +
     custom_theme()
-ggsave_with_defaults(generate_filename("alligatorSampleSize.png"), plot = p)
+
+paper_image <- p
+poster_image <- p
+ggsave_with_defaults(generate_filename("alligatorSampleSize.png"), plot = paper_image)
+ggsave_with_defaults(generate_filename("alligatorSampleSize-poster.png"), plot = poster_image)

### 2024-02-18 paperAndPoster/code/bayesianExample.R

@@ -27,7 +27,12 @@ p <- ggplot(df, aes(height, density, group = type, colour = type)) +
     custom_theme() +
     labs(x = "Height (cm)", y = "Density", colour = "Type") +
     scale_y_continuous(labels = NULL) +
-    scale_colour_grey() +
+    # scale_colour_grey() +
     theme(legend.position = c(0.8, 0.8), legend.background = element_rect(fill = 'white'))
 
-ggsave_with_defaults(generate_filename("bayesianExample.png"), plot = p)
+paper_image <- p + paper_colours()
+poster_image <- p + 
+    poster_colours() +
+
+ggsave_with_defaults(generate_filename("bayesianExample.png"), plot = paper_image)
+ggsave_with_defaults(generate_filename("bayesianExample-poster.png"), plot = poster_image)

### 2024-02-18 paperAndPoster/code/dinosaurs.R

@@ -69,7 +69,10 @@ p <- ggplot() +
     labs(x = "Age (years)", y = "Mass (kg)", title = "Prior 95% Quantiles") +
     custom_theme()
 
-ggsave_with_defaults(generate_filename("maiasauraPrior.png"), plot = p)
+paper_image <- p
+poster_image <- p
+ggsave_with_defaults(generate_filename("maiasauraPrior.png"), plot = paper_image)
+ggsave_with_defaults(generate_filename("maiasauraPrior-poster.png"), plot = poster_image)
 
 # now do the regression
 maiasaura$residual <- resid(population_fit)
@@ -125,14 +128,18 @@ for (i in 1:100) {
 p <- p +
     labs(title = "Maiasaura peeblesorum Data and Posterior Growth Curves") +
     theme(legend.position = c(0.7, 0.3), legend.background = element_rect(fill = 'white'))
-ggsave_with_defaults(generate_filename('maiasauraPosterior.png'), plot = p)
+
+paper_image <- p
+poster_image <- p
+ggsave_with_defaults(generate_filename('maiasauraPosterior.png'), plot = paper_image)
+ggsave_with_defaults(generate_filename('maiasauraPosterior-poster.png'), plot = poster_image)
 
 # actual amount of dimorphism
-p <- ggplot(data.frame(x = maiasaura_samples[['difference']]), aes(x)) +
-    geom_density(aes(y = after_stat(density))) +
-    labs(x = expression(L[l] - L[s]), y = "Density", title = "Posterior Distribution for Maiasaura Sexual Dimorphism") +
-    custom_theme()
-ggsave_with_defaults(generate_filename('maiasauraDimorphism.png'), plot = p)
+# p <- ggplot(data.frame(x = maiasaura_samples[['difference']]), aes(x)) +
+#     geom_density(aes(y = after_stat(density))) +
+#     labs(x = expression(L[l] - L[s]), y = "Density", title = "Posterior Distribution for Maiasaura Sexual Dimorphism") +
+#     custom_theme()
+# ggsave_with_defaults(generate_filename('maiasauraDimorphism.png'), plot = p)
 
 
 
@@ -207,7 +214,10 @@ p <- ggplot() +
     labs(x = "Age (years)", y = "Mass (kg)", title = "Prior 95% Quantiles") +
     custom_theme()
 
-ggsave_with_defaults(generate_filename("psittacosaurusPrior.png"), plot = p)
+paper_image <- p
[…]

### 2024-02-18 paperAndPoster/code/functions.R

@@ -130,3 +130,6 @@ ggsave_with_defaults <- function(filename, plot, width = 15, height = 8, dpi = 6
 }
 
 generate_filename <- function(name) sprintf("../images/%s", name)
+
+paper_colours <- function() scale_colour_grey()
+poster_colours <- function() scale_fill_viridis_d()

### 2024-02-19 paperAndPoster/poster.tex
feat: further poster edits (sabrina)

@@
   ] % See Section 4.1
-\block{Abstract}{While sexual dimorphism is common in extant taxa, detection in extinct taxa is made challenging by difficulties in determining the sex and size of organisms.
-Existing methods suffer from a lack of statistical power, making positive identification of dimorphism difficult.
-Herein is outline an modification to a method from \cite{saittaEffectSizeStatistical2020} which constructs sex-specific growth curves to determine sexual size dimorphism, but using Bayesian regression to construct the curves rather than standard non-linear regression.
-The method is shown to be robust and reliable, with the additional benefit of incorporating prior information to constrain dimorphism to biologically plausible levels.} % See Section 4.2
+\block{Abstract}{While sexual dimorphism is common in extant taxa, detection in extinct taxa is made challenging by difficulties in determining the sex and size of organisms combined with the low statistical power of existing methods.
+Herein is outlined a modification to the method from \cite{saittaEffectSizeStatistical2020} which constructs sex-specific growth curves to determine sexual size dimorphism, but using Bayesian regression to construct the curves rather than standard non-linear regression.
+The method is shown to be robust and reliable, with the additional benefit of incorporating prior information to constrain dimorphism to biologically plausible levels along with the incorporation of uncertainty to give a fuller understanding of the strength of our findings.} % See Section 4.2
 \begin{columns} % See Section 4.4
@@
     \item Sexual dimorphism is common in extant taxa, but positive examples in dinosaurs are rare
-    \item Determining sex and size of an extinct organism is difficult
-    \item Existing methods suffer from low statistical power and can be confounded by e.g. juveniles
+    \item Determining sex and size of an extinct organism is difficult, and existing methods suffer from low statistical power and confounding by e.g. juveniles
     \item Method in \cite{saittaEffectSizeStatistical2020}: construct growth curves for predicted male and females separately to measure dimorphism
@@
 }
-\block{Method}{
+\block[bodyinnersep=0mm]{Method}{
   \begin{enumerate}
@@
         \item Predict sex by assigning all samples above the population curve to one sex and all below to the other. 
-        \item \textcolor{red}{Fit separate growth curves to each predicted sex} $\to$ Create a posterior distribution for sex-specific parameters (Bayesian regression)
-        \item \textcolor{red}{Calculate maximum likelihood level of dimorphism} $\to$ Calculate posterior distribution for dimorphism
+        \item Create a posterior distribution for sex-specific parameters (Bayesian regression) (vs. fit separate growth curves to each predicted sex)
+        \item Calculate posterior distribution for dimorphism (vs. calculate maximum likelihood \& confidence interval for dimorphism)
   \end{enumerate}
@@
   \end{tikzfigure}
-For all data and code used here, along with additional analyses, see \url{https://github.com/EricRobertCampbell/aps-2024-poster-sexual-dimorphism}.
+For all data and code used here, along with additional analyses, see \\ \url{https://github.com/EricRobertCampbell/aps-2024-poster-sexual-dimorphism}.
 }
@@
       \begin{itemize}
-          \item To estimate mean human height, start with what we know about the height before seeing any data --- the \emph{prior}
-          \item A sample of heights is collected and the \emph{likelihood} of that sample for each of the potential mean heights is calculated
-          \item Combination of those, our final belief about the value of the mean height, is the \emph{posterior} distribution
+          \item To estimate mean human height, start with what we know about the height before seeing any data --- the \emph{prior}.
+          \item A sample of heights is collected and the \emph{likelihood} of that sample for each of the potential mean heights is calculated.
+          \item Combination of those, our final belief about the value of the mean height, is the \emph{posterior} distribution.
       \end{itemize}
@@
   \end{minipage}
+    $L$: asymptotic length; $A$: related to size at hatching; $K$: related to growth rate.
     \item Bayesian model with wide priors centred around the population-level curve values was used to recover the values \parencite{rCore, rstan}.
@@
 \column{0.333333333}
-\block{Results}{
+\block[bodyinnersep=0mm]{Results}{
   \begin{itemize}
@@
   \]
+  $L$: asymptotic mass; $q$: related to initial mass; $k$: growth rate.
   \end{itemize}
-\begin{tikzfigure}[Posterior distribution and data]
+\begin{tikzfigure}[Posterior growth curves and data]
   \centering
@@
 \end{tikzfigure}
+}
+\block[bodyinnersep=0mm]{Conclusion}{
   \begin{itemize}
-    \item Strong evidence for \maia{} (35\% -- 62\%), weak evidence for \psit{} (-2\% -- 31\%), and moderate evidence against \tyran{} (-7\% -- 13\%) dimorphism.
-    \item Benefits: incorporation of uncertainty and prior knowledge (constrain curve to be biologically feasible)
+    \item Strong evidence for \maia{} (35\% -- 62\%), weak evidence for \psit{} (-2\% -- 31\%), and moderate evidence against \tyran{} (-7\% -- 13\%) dimorphism (95\% credible intervals).
+    \item Benefits: incorporation of uncertainty (calibrate the strength of our findings) and prior knowledge (constrain curve to be biologically feasible)
   \end{itemize}
 }
-\block{Next Steps}{
+\block[bodyinnersep=0mm]{Next Steps}{
   \begin{itemize}

### 2024-02-19 paperAndPoster/code/alligatorEffectSize.R

@@ -61,17 +61,28 @@ sample_df$error <- sample_df$sample_diff - sample_df$actual_diff
 
 p <- ggplot(sample_df, aes(error, group = E, colour = E)) +
     geom_density(aes(y = after_stat(density))) +
+    # scale_color_distiller(
+    #     type = "seq",
+    #     direction = -1,
+    #     palette = "Greys"
+    # ) +
+    labs(x = "Error (Predicted - Actual)", y = "Density", title = "Effect Size on Dimorphism Error", colour = "Effect Size") +
+    scale_y_continuous(labels = NULL)
+paper_image <- p +
     scale_color_distiller(
         type = "seq",
         direction = -1,
         palette = "Greys"
     ) +
-    labs(x = "Error (Predicted - Actual)", y = "Density", title = "Effect Size on Dimorphism Error", colour = "Effect Size") +
-    scale_y_continuous(labels = NULL) +
-    custom_theme() +
-    theme(legend.position = c(0.2, 0.8), legend.background = element_rect(fill = 'white'))
-paper_image <- p
-poster_image <- p
+    paper_theme(legend.position = c(0.2, 0.8), legend.background = element_rect(fill = 'white'))
+poster_image <- p +
+    scale_color_distiller(
+        type = "seq",
+        direction = -1,
+        # palette = "Reds"
+        palette = "Greys"
+    ) +
+    poster_theme(legend.position = c(0.2, 0.8), legend.background = element_rect(fill = 'white'))
 ggsave_with_defaults(generate_filename("alligatorEffectSize.png"), plot = paper_image)
 ggsave_with_defaults(generate_filename("alligatorEffectSize-poster.png"), plot = poster_image)
 
@@ -104,16 +115,28 @@ p <- ggplot(error_by_error_df, aes(sex_prediction_accuracy, mean_error, colour =
     geom_point() +
     geom_errorbar(aes(ymin = lower, ymax = upper)) +
     geom_smooth(method = 'lm', se = FALSE, colour = 'black') +
+    # scale_color_distiller(
+    #     type = "seq",
+    #     direction = -1,
+    #     palette = "Greys"
+    # ) +
+    scale_x_continuous(labels = scales::percent) +
+    labs(x = "Sex Prediction Accuracy", y = "Error (Predicted - Actual)", colour = "Effect Size", title = "Relationship Between Dimorphism Error and Sex Prediction Accuracy")
+
+paper_image <- p +
     scale_color_distiller(
         type = "seq",
[…]

### 2024-02-19 paperAndPoster/code/alligatorMethod.R

@@ -17,13 +17,11 @@ p <- ggplot(combined_data, aes(age, length)) +
     annotate('label', label = "Predicted Male", x = 25, y = 3.7, size = unit(8, 'pt'), fill = 'white', label.size = NA) +
     annotate('label', label = "Predicted Female", x = 25, y = 1.2, size = unit(8, 'pt'), fill = 'white', label.size = NA) +
     annotate('label', label = "Population Curve", x = 35, y = 2.8, size = unit(8, 'pt'), fill = 'white', label.size = NA) +
-    scale_colour_grey() +
-    scale_fill_grey() +
-    custom_theme() +
-    labs(x = "Age (years)", y = "Length (m)", title = "Alligator Population and Curve", colour = "Actual Sex", shape = "Actual Sex") +
-    theme(legend.position = c(0.85, 0.25), legend.background = element_rect(fill = 'white'))
+    labs(x = "Age (years)", y = "Length (m)", title = "Alligator Population and Curve", colour = "Actual Sex", shape = "Actual Sex")
 
-paper_image <- p
-poster_image <- p
+paper_image <- paper_colours(p) + 
+    paper_theme(legend.position = c(0.85, 0.25), legend.background = element_rect(fill = 'white'))
+poster_image <- poster_colours(p) + 
+    poster_theme(legend.position = c(0.85, 0.25), legend.background = element_rect(fill = 'white'))
 ggsave_with_defaults(generate_filename("alligatorMethod.png"), plot = paper_image)
 ggsave_with_defaults(generate_filename("alligatorMethod-poster.png"), plot = poster_image)

### 2024-02-19 paperAndPoster/code/alligatorSampleSize.R

@@ -77,10 +77,11 @@ p <- ggplot(summary_df, aes(sample_size, mean)) +
     geom_pointrange(aes(ymin = lower, ymax = upper)) +
     geom_hline(yintercept = actual_diff, linewidth = 2, linetype = 'dashed') +
     annotate('label', label = "Actual Level", x = 4.5, y = 0.7, size = unit(8, 'pt'), fill = 'white', label.size = NA) +
-    labs(x = "Total Sample Size", y = "Dimorphism Level (m)", title = "Dimorphism Level (Mean and 95% Credible Interval) and Sample Size") +
-    custom_theme()
+    labs(x = "Total Sample Size", y = "Dimorphism Level (m)", title = "Dimorphism Level (Mean and 95% Credible Interval) and Sample Size")
 
-paper_image <- p
-poster_image <- p
+paper_image <- paper_colours(p) +
+    paper_theme()
+poster_image <- poster_colours(p) +
+    poster_theme()
 ggsave_with_defaults(generate_filename("alligatorSampleSize.png"), plot = paper_image)
 ggsave_with_defaults(generate_filename("alligatorSampleSize-poster.png"), plot = poster_image)

### 2024-02-19 paperAndPoster/code/bayesianExample.R

@@ -24,15 +24,15 @@ df <- data.frame(
 
 p <- ggplot(df, aes(height, density, group = type, colour = type)) +
     geom_line(linewidth = 2) +
-    custom_theme() +
     labs(x = "Height (cm)", y = "Density", colour = "Type") +
     scale_y_continuous(labels = NULL) +
     # scale_colour_grey() +
-    theme(legend.position = c(0.8, 0.8), legend.background = element_rect(fill = 'white'))
+    theme()
 
-paper_image <- p + paper_colours()
-poster_image <- p + 
-    poster_colours() +
+paper_image <- paper_colours(p) +
+    paper_theme(legend.position = c(0.8, 0.8), legend.background = element_rect(fill = 'white'))
+poster_image <- poster_colours(p) + 
+    poster_theme(legend.position = c(0.8, 0.8), legend.background = element_rect(fill = 'white'))
 
 ggsave_with_defaults(generate_filename("bayesianExample.png"), plot = paper_image)
 ggsave_with_defaults(generate_filename("bayesianExample-poster.png"), plot = poster_image)

### 2024-02-19 paperAndPoster/code/dinosaurs.R

@@ -12,8 +12,7 @@ maiasaura <- data.frame(
 
 maiasaura_plot <- ggplot(maiasaura, aes(age, mass)) +
     geom_point() +
-    labs(x = "Age (years)", y = "Mass (kg)", title = "Maiasaura peeblesorum") +
-    custom_theme()
+    labs(x = "Age (years)", y = "Mass (kg)", title = "Maiasaura peeblesorum")
 
 initial_maiasaura_params <- list(
     L=2500,
@@ -66,13 +65,13 @@ for (age in unique(curve_data$age)) {
 p <- ggplot() +
     geom_point(data = maiasaura, mapping = aes(age, mass)) +
     geom_ribbon(data = range_df, mapping = aes(x = age, ymin = lower, ymax = upper), alpha = 0.2) +
-    labs(x = "Age (years)", y = "Mass (kg)", title = "Prior 95% Quantiles") +
-    custom_theme()
+    labs(x = "Age (years)", y = "Mass (kg)", title = "Prior 95% Quantiles")
 
-paper_image <- p
-poster_image <- p
+paper_image <- poster_colours(p) +
+    poster_theme()
+# poster_image <- p
 ggsave_with_defaults(generate_filename("maiasauraPrior.png"), plot = paper_image)
-ggsave_with_defaults(generate_filename("maiasauraPrior-poster.png"), plot = poster_image)
+# ggsave_with_defaults(generate_filename("maiasauraPrior-poster.png"), plot = poster_image)
 
 # now do the regression
 maiasaura$residual <- resid(population_fit)
@@ -102,10 +101,7 @@ maiasaura_samples <- extract(maiasaura.model)
 lapply(maiasaura_samples, head)
 
 p <- ggplot() +
-    custom_theme() +
-    geom_point(maiasaura, mapping = aes(age, mass, colour = sex), size = 3) +
-    scale_colour_grey() +
-    labs(x = "Age (years)", y = "Mass (kg)", colour = "Sex")
+    labs(x = "Age (years)", y = "Mass (kg)", colour = "Sex", title = "Maiasaura peeblesorum")
 
 # draw in samples from the male and female curves
 for (i in 1:100) {
@@ -121,16 +117,17 @@ for (i in 1:100) {
     curve_mass_large <- generalized_logistic(curve_ages, L = L_large, k = k_large, q = q_large)
 
     p <- p + 
[…]

### 2024-02-19 paperAndPoster/code/functions.R

@@ -1,4 +1,3 @@
-
 library(ggplot2)
 library(FSA) # for the vbStart function to find good parameters for the von Bertalanffy function
 library(minpack.lm) # a more robust version of nls for non-linear curve fitting to avoid problems with e.g. very small sample sizes
@@ -9,27 +8,56 @@ rstan_options(auto_write = TRUE)
 
 source("constants.R")
 
-custom_theme <- function() {
+base_theme <- function() {
   theme_minimal() +
     theme(
       panel.background = element_rect(fill = "white"),
       panel.grid.major = element_line(color = alpha("black", 0.5), linetype = "dotted", linewidth = 0.5),
       panel.grid.minor = element_blank(),
-      axis.text = element_text(size = 12),  # Adjust the font size of axis labels
-      axis.title = element_text(size = 16),  # Adjust the font size of axis titles
-      plot.title = element_text(size = 20, hjust = 0.5),  # Adjust the font size and center the plot title
-      plot.subtitle = element_text(size = 16, hjust = 0.5)  # Adjust the font size and center the plot subtitle
     )
 }
 
-paper_colours <- function() {
+paper_theme <- function(...) base_theme() +
+    theme(
+      axis.text = element_text(size = 12),  # Adjust the font size of axis labels
+      axis.title = element_text(size = 16),  # Adjust the font size of axis titles
+      plot.title = element_text(size = 20, hjust = 0.5),  # Adjust the font size and center the plot title
+      plot.subtitle = element_text(size = 16, hjust = 0.5),  # Adjust the font size and center the plot subtitle
+      ...
+    )
+
+poster_theme <- function(...) base_theme() + 
+    theme(
+        axis.text = element_text(size = 16),  # Adjust the font size of axis labels
+        axis.title = element_text(size = 20),  # Adjust the font size of axis titles
+        plot.title = element_text(size = 24, hjust = 0.5),  # Adjust the font size and center the plot title
+        plot.subtitle = element_text(size = 20, hjust = 0.5),  # Adjust the font size and center the plot subtitle
+        legend.title = element_text(size = 20),
+        legend.text = element_text(size = 14),  # Adjust text size
+        ...
+    )
+
+
+
+cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
[…]

### 2024-02-20 paperAndPoster/poster.tex
feat: playing around with layout and edits (kristy)

@@
 \addbibresource{bibliography.bib}
+\usepackage{enumitem}
+\setlist{
+  itemsep=0pt,
+  partopsep=0pt,
+}
 \input{common.tex}
@@
 }}
-\usetheme{Simple} % See Section 5
+
+% based on Denmark
+\definecolorstyle{MyColourStyle}{
+    % Define default colors
+    % PurpleGrayBlue
+    \definecolor{colorOne}{HTML}{AE0D45}
+    \definecolor{colorTwo}{HTML}{7F8897}
+    \definecolor{colorThree}{HTML}{C8512D}
+}{
+     % Background Colors
+    \colorlet{backgroundcolor}{white}
+    \colorlet{framecolor}{white}
+    % Title Colors
+    \colorlet{titlebgcolor}{colorOne}
+    \colorlet{titlefgcolor}{white}
+    % Block Colors
+    \colorlet{blocktitlebgcolor}{colorTwo}
+    \colorlet{blocktitlefgcolor}{colorOne}
+    \colorlet{blockbodybgcolor}{white}
+    \colorlet{blockbodyfgcolor}{black}
+    % Innerblock Colors
+    \colorlet{innerblocktitlebgcolor}{colorThree}
+    \colorlet{innerblocktitlefgcolor}{white}
+    \colorlet{innerblockbodybgcolor}{white}
+    \colorlet{innerblockbodyfgcolor}{black}
+    % Note colors
+    \colorlet{notefgcolor}{black}
+    \colorlet{notebgcolor}{colorTwo!50!white}
+    \colorlet{notefrcolor}{colorTwo!50!white}
+ }
+
+\definelayouttheme{MyTheme}{ % copied from the definition of the 'Simple' style to allow customization
+    \usecolorstyle{MyColourStyle}
+    \usebackgroundstyle{Default}
+    \usetitlestyle{Default}
+    \useblockstyle{Minimal}
+    \useinnerblockstyle{Default}
+    \usenotestyle{Default}
+}
+\usetheme{MyTheme}
+% \usetheme{Simple} % See Section 5
+% \usecolorstyle[colorPalette=BrownBlueOrange]{Default}
+% \usecolorpalette{BlueGrayOrange}
 
@@
   ] % See Section 4.1
-\block{Abstract}{While sexual dimorphism is common in extant taxa, detection in extinct taxa is made challenging by difficulties in determining the sex and size of organisms combined with the low statistical power of existing methods.
+\block{Abstract}{While sexual dimorphism is common in extant taxa, detection in extinct ones is made challenging by difficulties in determining the sex and size of fossil organisms combined with the low statistical power of existing methods.
 Herein is outlined a modification to the method from \cite{saittaEffectSizeStatistical2020} which constructs sex-specific growth curves to determine sexual size dimorphism, but using Bayesian regression to construct the curves rather than standard non-linear regression.
-The method is shown to be robust and reliable, with the additional benefit of incorporating prior information to constrain dimorphism to biologically plausible levels along with the incorporation of uncertainty to give a fuller understanding of the strength of our findings.} % See Section 4.2
+The method is shown to be robust and reliable on both simulated and actual populations, with the additional benefit of incorporating prior information to constrain dimorphism to biologically plausible levels along with the incorporation of uncertainty to give a fuller understanding of the strength of the results.} % See Section 4.2
 \begin{columns} % See Section 4.4
@@
     \item Sexual dimorphism is common in extant taxa, but positive examples in dinosaurs are rare
-    \item Determining sex and size of an extinct organism is difficult, and existing methods suffer from low statistical power and confounding by e.g. juveniles
-    \item Method in \cite{saittaEffectSizeStatistical2020}: construct growth curves for predicted male and females separately to measure dimorphism
-    \item Can suffer from lack of numerical convergence and implausible predictions (e.g. negative masses), particularly for small sample sizes
-    \item Proposed modification: use Bayesian regression to estimte growth curves
+    \item Levels of dimorphism can correlate with  ecological behaviours: monogamy, group size, inter- and intrasexual competition, \&c., potentially providing insight into dinosaur ecologies and social structure
+    \item Determining sex and size of an extinct organism is difficult, and existing methods to determine dimorphism suffer from low statistical power and confounding by e.g. presence of juveniles
+    \item Method in \cite{saittaEffectSizeStatistical2020}: construct growth curves for predicted male and females separately to measure dimorphism.
+This method can suffer from lack of numerical convergence and implausible predictions (e.g.
+negative masses), particularly for small sample sizes
+    \item Proposed modification: use Bayesian regression to estimate growth curves, getting as a result a posterior distribution for level of dimorphism rather than a point estimate or range
   \end{itemize}
@@
   \end{enumerate}
-  \begin{tikzfigure}[Simulated Alligator Populations \& Method]
+  \begin{tikzfigure}[Simulated alligator populations \& method, demonstrating the actual male and female populations, the predicted sex, and the population-level curve used for the sex prediction]
     \includegraphics[width = 0.9\colwidth]{images/alligatorMethod-poster.png}
@@
   \end{itemize}
-    \begin{tikzfigure}[Verification results]
+    \begin{tikzfigure}[Verification results.
+The method becomes more accurate with larger sample sizes, although the 95\% credible interval consistently includes the true value.
+Due to the sex prediction method, it tends to overestimate small amounts of dimorphism but accurately predict large ones.
+Much of the error in the level of dimorphism is due to the sex prediction accuracy, which is worse at lower levels of dimorphism.]
       \includegraphics[width = 0.4\colwidth]{images/alligatorSampleSize-poster.png}
@@
   \end{itemize}
-\begin{tikzfigure}[Posterior growth curves and data]
+\begin{tikzfigure}[Raw data and a random sample of growth curves for the dinosaurs.
+Since we lack data on the actual sexes, $l$ (``larger'') and $s$ (``smaller'') are used as placeholders.
+A clear separation is shown in \maia{}, while there is considerably more overlap in \psit{} and \tyran{}.
+\psit{} lacks individuals in the asymptotic portion of the growth curve, while \tyran{} lacks both very young and very old individuals.]
   \centering
@@
 
-\begin{tikzfigure}[Posterior relative dimorphism]
+\begin{tikzfigure}[Posterior distribution for relative dimorphism (larger sex as percentage of smaller one) for the three dinosaur species.]
   \centering
@@
   \begin{itemize}
+    \item Method is effective for actual dinosaur data, even at low sample sizes ($n=8$ for \tyran{})
     \item Strong evidence for \maia{} (35\% -- 62\%), weak evidence for \psit{} (-2\% -- 31\%), and moderate evidence against \tyran{} (-7\% -- 13\%) dimorphism (95\% credible intervals).

### 2024-02-20 paperAndPoster/code/dinosaurs.R

@@ -458,7 +458,7 @@ saitta_dimorphism_df <- data.frame(
 
 p <- ggplot(dimorphism_df, aes(x = x, colour = species)) +
     geom_density(aes(y = after_stat(density), fill = species), alpha = 0.2, linewidth = 2) +
-    geom_vline(data = saitta_dimorphism_df, mapping = aes(xintercept = dimorphism, colour = species, linetype = "Saitta et al (2020)"), linewidth = 2) +
+    geom_vline(data = saitta_dimorphism_df, mapping = aes(xintercept = dimorphism, colour = species, linetype = "Saitta et al. 2020"), linewidth = 2) +
     scale_linetype_manual(values = c("Saitta et al (2020)" = 'dashed')) +
     scale_x_continuous(labels = scales::percent) +
     labs(x = "Percent Dimorphism", y = "Density", title = "A Comparison of Different Distributions of Dimorphism", colour = "Species", fill = "Species", linetype = NULL)

### 2024-02-22 paperAndPoster/poster.tex
chore: minor mucking about

@@
 ]{tikzposter} % See Section 3
+\usetikzlibrary{decorations.footprints}
+\usetikzlibrary{decorations.markings}
 \usepackage{xcolor}
@@
 
+\defineblockstyle{MyBlockStyle}{
+    titlewidthscale=1, bodywidthscale=1, titleleft,
+    titleoffsetx=0pt, titleoffsety=0pt, bodyoffsetx=0pt, bodyoffsety=0pt,
+    bodyverticalshift=0pt, roundedcorners=0, linewidth=0.2cm,
+    titleinnersep=1cm, bodyinnersep=1cm
+}{
+    \begin{scope}[line width=\blocklinewidth, rounded corners=\blockroundedcorners]
+       \ifBlockHasTitle %
+           \draw[draw=none]%, fill=blockbodybgcolor]
+               (blockbody.south west) rectangle (blocktitle.north east);
+          %  \draw[color=blocktitlebgcolor, loosely dashed, thick]
+           \draw[color=blocktitlebgcolor, loosely dashed]
+          %  \draw[color=blocktitlebgcolor, decoration={footprints, stride length=50pt, foot sep=0pt, foot of=bird}, decorate]
+               (blocktitle.south west) -- (blocktitle.south east);%
+       \else
+             \draw[draw=none]%, fill=blockbodybgcolor]
+                 (blockbody.south west) rectangle (blockbody.north east);
+        \fi
+    \end{scope}
+}
+
 \definelayouttheme{MyTheme}{ % copied from the definition of the 'Simple' style to allow customization
@@
     \usetitlestyle{Default}
-    \useblockstyle{Minimal}
+    % \useblockstyle{Minimal}
+    \useblockstyle{MyBlockStyle}
     \useinnerblockstyle{Default}
@@
 \block{Abstract}{While sexual dimorphism is common in extant taxa, detection in extinct ones is made challenging by difficulties in determining the sex and size of fossil organisms combined with the low statistical power of existing methods.
-Herein is outlined a modification to the method from \cite{saittaEffectSizeStatistical2020} which constructs sex-specific growth curves to determine sexual size dimorphism, but using Bayesian regression to construct the curves rather than standard non-linear regression.
+Herein is outlined a modification to the method from \cite{saittaEffectSizeStatistical2020} employing Bayesian regression instead of standard non-linear regression to construct sex-specific growth curves for quantifying sexual size dimorphism in dinosaurs.
+% which constructs sex-specific growth curves to determine sexual size dimorphism, but using Bayesian regression to construct the curves rather than standard non-linear regression.
  The method is shown to be robust and reliable on both simulated and actual populations, with the additional benefit of incorporating prior information to constrain dimorphism to biologically plausible levels along with the incorporation of uncertainty to give a fuller understanding of the strength of the results.} % See Section 4.2
@@
     \item Levels of dimorphism can correlate with  ecological behaviours: monogamy, group size, inter- and intrasexual competition, \&c., potentially providing insight into dinosaur ecologies and social structure
-    \item Determining sex and size of an extinct organism is difficult, and existing methods to determine dimorphism suffer from low statistical power and confounding by e.g. presence of juveniles
+    \item Determining sex and size of an extinct organism is difficult, and existing methods to determine dimorphism (Hartigans' dip test, $t$ tests) suffer from low statistical power and confounding by e.g.
+presence of juveniles
     \item Method in \cite{saittaEffectSizeStatistical2020}: construct growth curves for predicted male and females separately to measure dimorphism.
@@
     \includegraphics[width = 0.9\colwidth]{images/alligatorMethod-poster.png}
-  \end{tikzfigure}
+  \end{tikzfigure}%
 For all data and code used here, along with additional analyses, see \\ \url{https://github.com/EricRobertCampbell/aps-2024-poster-sexual-dimorphism}.
@@
         \centering
-        \includegraphics[width = \textwidth]{images/bayesianExample-poster.png}
+        \includegraphics[width = \textwidth]{images/bayesianExample-poster.png}%
         \label{fig:bayesianExplanation}
-      \end{tikzfigure}
-    \end{minipage}
+      \end{tikzfigure}%
+    \end{minipage}%
     \begin{minipage}[t]{0.45\colwidth}
@@
       \end{itemize}
-    \end{minipage}
+    \end{minipage}%
   \begin{itemize}
@@
   \end{minipage}
-    $L$: asymptotic length; $A$: related to size at hatching; $K$: related to growth rate.
+      \makebox[0.9\colwidth]{$L$: asymptotic length; $A$: related to size at hatching; $K$: related to growth rate.}
     \item Bayesian model with wide priors centred around the population-level curve values was used to recover the values \parencite{rCore, rstan}.
@@
 Much of the error in the level of dimorphism is due to the sex prediction accuracy, which is worse at lower levels of dimorphism.]
-      \includegraphics[width = 0.4\colwidth]{images/alligatorSampleSize-poster.png}
-      \includegraphics[width = 0.4\colwidth]{images/alligatorEffectSize-poster.png}
+      \includegraphics[width = 0.4\colwidth]{images/alligatorSampleSize-poster.png}%
+      \includegraphics[width = 0.4\colwidth]{images/alligatorEffectSize-poster.png}%
 
-      \includegraphics[width = 0.45\colwidth]{images/alligatorSexPredictionAccuracyDimorphismError-poster.png}
-    \end{tikzfigure}
+      \includegraphics[width = 0.45\colwidth]{images/alligatorSexPredictionAccuracyDimorphismError-poster.png}%
+    \end{tikzfigure}%
 }
@@
   \]
-  $L$: asymptotic mass; $q$: related to initial mass; $k$: growth rate.
+  \makebox[0.9\colwidth]{$L$: asymptotic mass; $q$: related to initial mass; $k$: growth rate.}
   \end{itemize}
@@
     \centering
-    \includegraphics[width=\textwidth]{images/maiasauraPosterior-poster.png}
-  \end{minipage}
+    \includegraphics[width=\textwidth]{images/maiasauraPosterior-poster.png}%
+  \end{minipage}%
   \begin{minipage}[b]{0.3\colwidth}
     \centering
-    \includegraphics[width=\textwidth]{images/psittacosaurusPosterior-poster.png}
-  \end{minipage}
+    \includegraphics[width=\textwidth]{images/psittacosaurusPosterior-poster.png}%
+  \end{minipage}%
   \begin{minipage}[b]{0.3\colwidth}
     \centering
-    \includegraphics[width=\textwidth]{images/tyrannosaurPosterior-poster.png}
-  \end{minipage}
-\end{tikzfigure}
-
+    \includegraphics[width=\textwidth]{images/tyrannosaurPosterior-poster.png}%
+  \end{minipage}%
+\end{tikzfigure}%
 \begin{tikzfigure}[Posterior distribution for relative dimorphism (larger sex as percentage of smaller one) for the three dinosaur species.]
   \centering
-  \includegraphics[width=0.9\colwidth]{images/combinedDimorphism-poster.png}
-\end{tikzfigure}
+  \includegraphics[width=0.9\colwidth]{images/combinedDimorphism-poster.png}%
+\end{tikzfigure}%
 }
@@
     \item Incorporate measurement uncertainty (age, size) into the model
-    \item Improve sex prediction (clustering algorithms, incorporate additional features)
+    \item \textbf{Improve sex prediction (clustering algorithms, incorporate additional features)}
     \item Use of mixture models to avoid assuming dimorphism

### 2024-02-22 paperAndPoster/code/dinosaurs.R

@@ -459,7 +459,7 @@ saitta_dimorphism_df <- data.frame(
 p <- ggplot(dimorphism_df, aes(x = x, colour = species)) +
     geom_density(aes(y = after_stat(density), fill = species), alpha = 0.2, linewidth = 2) +
     geom_vline(data = saitta_dimorphism_df, mapping = aes(xintercept = dimorphism, colour = species, linetype = "Saitta et al. 2020"), linewidth = 2) +
-    scale_linetype_manual(values = c("Saitta et al (2020)" = 'dashed')) +
+    scale_linetype_manual(values = c("Saitta et al. 2020" = 'dashed')) +
     scale_x_continuous(labels = scales::percent) +
     labs(x = "Percent Dimorphism", y = "Density", title = "A Comparison of Different Distributions of Dimorphism", colour = "Species", fill = "Species", linetype = NULL)
 paper_image <- paper_colours(p) +
